
-------------------------------------------------------------------------------------------------------
  Google Sheet Function Format Examples:
  
    = GOOGLEFINANCE("NZE:MDZ","all",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
      
    Gives 6 columns: "Date","Open","High","Low","Close","Volume"
      
    = GOOGLEFINANCE("NZE:MDZ","close",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
    
    Gives 2 columns: "Date","Close"
-------------------------------------------------------------------------------------------------------

# Load Tickers
```{r}
rm(list=ls())
df = read.csv("NZX.csv")
```


# Generate Excel Formulas for Downloading Tickers to Upload to Google Sheets 
```{r}
# define corresponding exchanges
##########################################################################################################
# create google sheet formulas for ETF tickers
##########################################################################################################
googlefinance_single = function(ticker   = "NZ50G",
                                exchange = "NZE",
                                start    = "DATE(2000,1,1)",
                                stop     = paste0("DATE(",gsub("-",",",Sys.Date()),")")) {
  return(
    paste0( "= GOOGLEFINANCE(\"" , exchange , ":" , ticker, "\",\"all\"," , start , "," , stop , ",\"DAILY\")" )
  )
}

# loop through tickers and generate excel formula
xlsx = c()
for (i in 93:184) {
  
  # input with ticker and exchange symbols
  s = googlefinance_single(df$Code[i], "NZE")

  # 6 column space between strings
  xlsx = c(xlsx,c(s,rep("",5)))

}

# write to output, default to desktop
write.csv(t(xlsx),file.path(Sys.getenv("USERPROFILE"),"Desktop","temp.csv"),row.names=FALSE)
```


# Manual Step for Downloading All Selected Ticker Data
1) Upload file generated in the code block above is uploaded onto google drive 
2) Converet file to a google sheet (formula will execute automatically)
3) Go to "File" -> "Publish to the Web" with type = ".csv", then click "Publish"
4) Using the link obtained from publishing, copy paste URL into new webpage and download the file


# Process and Save Ticker Data Downloaded from Google Sheets Chunks
```{r}
setwd(file.path(Sys.getenv("USERPROFILE"),"Desktop"))

# loop through each doc
j = 2      # Manually Adjust This
count = 93 # Manually Adjust This

# read donwloaded file from desktop
path    = paste0("temp - temp ",j,".csv")
all_dat = read.csv(path,sep=",",header=TRUE,stringsAsFactors=FALSE)

# loop through every 6 columns and save to csv
for (i in seq(1,ncol(all_dat),by=6)) {
  
  # extract data for 1 ticker
  temp = all_dat[2:nrow(all_dat),i:(i+5)]      # get relevant columns
  colnames(temp) = tolower(all_dat[1,i:(i+5)]) # define column names
  temp = temp[temp[,1]!="",]                   # remove NA rows
  
  # change format of dates
  col1 = unlist(strsplit(temp[,1]," "))[c(TRUE,FALSE)]

  if (!is.null(col1)) {
  
    # format columns
    temp[,1]   = as.Date(col1,format="%d/%m/%Y") # as.Date(col1,format="%m/%d/%Y") #
    temp[,2:6] = as.numeric(unlist(temp[,2:6]))
  
    # write to file
    write.csv(temp,paste0("nzx stocks/",df$Code[count],".csv"),row.names=FALSE)
    
  }
  
  count = count + 1
  
}
```
