

-------------------------------------------------------------------------------------------------------
  NYSE Ticker List of Symbols
    
    https://www.interactivebrokers.com/en/index.php?f=2222&exch=nyse&showcategories=
-------------------------------------------------------------------------------------------------------


# Get All NYSE Symbols
```{r}
# read nasdaq ticker data
txt = readLines("nysearca.txt")

# change classes
df = data.frame(Symbol=txt)
df$Data       = NA
```


-------------------------------------------------------------------------------------------------------
  Google Sheet Function Format Examples:
  
    = GOOGLEFINANCE("NZE:MDZ","all",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
      
    Gives 6 columns: "Date","Open","High","Low","Close","Volume"
      
    = GOOGLEFINANCE("NZE:MDZ","close",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
    
    Gives 2 columns: "Date","Close"
-------------------------------------------------------------------------------------------------------


# Generate Excel Formulas for Downloading Tickers to Upload to Google Sheets 
```{r}
# need to iterate through each one, one data at a time due to memory restrictions
i1 = 1   # 1    151  301  451  601  751  901 1051 1201 1351 1501 1651 1801 1951 2101 2251 2401 2551 2701 2851
i2 = 150 # 150  300  450  600  750  900 1050 1200 1350 1500 1650 1800 1950 2100 2250 2400 2550 2700 2850 3000

# define corresponding exchanges
##########################################################################################################
# create google sheet formulas for ETF tickers
##########################################################################################################
googlefinance_single = function(ticker   = "NZ50G",
                                exchange = "NZE",
                                start    = "DATE(2000,1,1)",
                                stop     = paste0("DATE(",gsub("-",",",Sys.Date()),")")) {
  return(
    paste0( "= GOOGLEFINANCE(\"" , exchange , ":" , ticker, "\",\"all\"," , start , "," , stop , ",\"DAILY\")" )
  )
}

# loop through tickers and generate excel formula
xlsx = c()
for (i in i1:i2) {
  
  # input with ticker and exchange symbols
  s = googlefinance_single(df$Symbol[i], "NYSE")

  # 6 column space between strings
  xlsx = c(xlsx,c(s,rep("",5)))

}

# write to output, default to desktop
write.csv(t(xlsx),file.path(Sys.getenv("USERPROFILE"),"Desktop","temp.csv"),row.names=FALSE)
```


# Manual Step for Downloading All Selected Ticker Data
1) Upload file generated in the code block above is uploaded onto google drive 
2) Converet file to a google sheet (formula will execute automatically)
3) Go to "File" -> "Publish to the Web" with type = ".csv", then click "Publish"
4) Using the link obtained from publishing, copy paste URL into new webpage and download the file


# Process and Save Ticker Data Downloaded from Google Sheets Chunks
```{r}
setwd(file.path(Sys.getenv("USERPROFILE"),"Desktop"))

count = 1

# loop through each doc
for (j in 1:18) {

  print(j)
  # read donwloaded file from desktop
  path    = paste0("temp - temp ",j,".csv")
  all_dat = read.csv(path,sep=",",header=TRUE,stringsAsFactors=FALSE)
  
  # loop through every 6 columns and save to csv
  for (i in seq(1,ncol(all_dat),by=6)) {
    
    # extract data for 1 ticker
    temp = all_dat[2:nrow(all_dat),i:(i+5)]      # get relevant columns
    colnames(temp) = tolower(all_dat[1,i:(i+5)]) # define column names
    temp = temp[temp[,1]!="",]                   # remove NA rows
    
    # change format of dates
    col1 = unlist(strsplit(temp[,1]," "))[c(TRUE,FALSE)]
  
    if (!is.null(col1)) {
    
      # format columns
      if (j == 4) {
        temp[,1]   = as.Date(col1,format="%m/%d/%Y")
      } else {
        temp[,1]   = as.Date(col1,format="%d/%m/%Y")
      }
      temp[,2:6] = as.numeric(unlist(temp[,2:6]))
    
      # write to file
      write.csv(temp,paste0("nyse stocks/",df$Symbol[count],".csv"),row.names=FALSE)
      
      # if there is data for this ticker
      df$Data[count] = "Y"
      
    } else {
      
      # if there is no data for this ticker
      df$Data[count] = "N"
      
    }
    
    count = count + 1
      
  }

}

# Save NASDAQ Ticker Symbols and Info into Spreadsheet
write.csv(df,"NYSE.csv",row.names=FALSE)
```


-------------------------------------------------------------------------------------------------------
  Individual Stock Data
    
    https://finviz.com/quote.ashx?t=AACQ
-------------------------------------------------------------------------------------------------------


# Add Market Caps
```{r}
rm(list=ls())

# Load data
nyse = read.csv("NYSE.csv",sep=",",header=TRUE,stringsAsFactors=FALSE)
nyse = nyse[nyse$Data == "Y",]

# define new columns
nyse$Cap   = NA
nyse$Float = NA

# append new data to data frame
for (i in 1:nrow(nyse)) {
  
  print(i)
  
  # read webpage
  webpage = tryCatch({readLines(paste0("https://finviz.com/quote.ashx?t=",nyse$Symbol[i]))},
                      error   = function(cond) {return(NA)}
                     )
  
  if (!is.na(webpage)) {

    # market cap data
    line  = webpage[grepl("Market Cap",webpage)]
    start = gregexpr("<b>",line)[[1]][1]
    end   = gregexpr("</b>",line)[[1]][1]
    
    nyse$Cap[i] = substring(line,start+3,end-1)
    
    # float data in millions
    line  = webpage[grepl("Shs Float",webpage)]
    start = gregexpr("<b>",line)[[1]][1]
    end   = gregexpr("</b>",line)[[1]][1]
    
    nyse$Float[i] = substring(line,start+3,end-1)
    
  }

}

nyse[is.na(nyse)] = "-"

# change cap and float to millions
nyse$Cap   = as.numeric(substr(nyse$Cap,1,nchar(nyse$Cap)-1))     * ifelse(grepl("M",nyse$Cap),1,1000)
nyse$Float = as.numeric(substr(nyse$Float,1,nchar(nyse$Float)-1)) * ifelse(grepl("M",nyse$Float),1,1000)

# Save updated info
write.csv(nyse,"NYSE.csv",row.names=FALSE)
```
