

-------------------------------------------------------------------------------------------------------
  Nasdaq Ticker List of Symbols
    
    https://www.nasdaqtrader.com/trader.aspx?id=symbollookup
-------------------------------------------------------------------------------------------------------


# Get All NASDAQ Symbols
```{r}
# read nasdaq ticker data
txt = readLines("nasdaq.txt")

# column names
cols = strsplit(txt[1],"\\|")[[1]]

# convert to data frame
df = data.frame(matrix(unlist(lapply(txt[2:length(txt)], function(x) strsplit(x,"\\|")[[1]])),ncol=length(cols),byrow=TRUE))
colnames(df) = cols

# filter
df = df[df$`ETF`=="N",]
df = df[df$`NextShares`=="N",]

# change classes
df$Symbol     = as.character(df$Symbol)
df$Data       = NA
row.names(df) = NULL
```


-------------------------------------------------------------------------------------------------------
  Google Sheet Function Format Examples:
  
    = GOOGLEFINANCE("NZE:MDZ","all",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
      
    Gives 6 columns: "Date","Open","High","Low","Close","Volume"
      
    = GOOGLEFINANCE("NZE:MDZ","close",DATE(1970,1,1),DATE(2020,6,7),"DAILY") 
    
    Gives 2 columns: "Date","Close"
-------------------------------------------------------------------------------------------------------


# Generate Excel Formulas for Downloading Tickers to Upload to Google Sheets 
```{r}
# need to iterate through each one, one data at a time due to memory restrictions
i1 = 1   # 1    151  301  451  601  751  901 1051 1201 1351 1501 1651 1801 1951 2101 2251 2401 2551 2701 2851
i2 = 150 # 150  300  450  600  750  900 1050 1200 1350 1500 1650 1800 1950 2100 2250 2400 2550 2700 2850 3000

# define corresponding exchanges
##########################################################################################################
# create google sheet formulas for ETF tickers
##########################################################################################################
googlefinance_single = function(ticker   = "NZ50G",
                                exchange = "NZE",
                                start    = "DATE(1995,1,1)",
                                stop     = paste0("DATE(",gsub("-",",",Sys.Date()),")")) {
  return(
    paste0( "= GOOGLEFINANCE(\"" , exchange , ":" , ticker, "\",\"all\"," , start , "," , stop , ",\"DAILY\")" )
  )
}

# loop through tickers and generate excel formula
xlsx = c()
for (i in i1:i2) {
  
  # input with ticker and exchange symbols
  s = googlefinance_single(df$`Symbol`[i], "NASDAQ")

  # 6 column space between strings
  xlsx = c(xlsx,c(s,rep("",5)))

}

# write to output, default to desktop
write.csv(t(xlsx),file.path(Sys.getenv("USERPROFILE"),"Desktop","temp.csv"),row.names=FALSE)
```


# Manual Step for Downloading All Selected Ticker Data
1) Upload file generated in the code block above is uploaded onto google drive 
2) Converet file to a google sheet (formula will execute automatically)
3) Go to "File" -> "Publish to the Web" with type = ".csv", then click "Publish"
4) Using the link obtained from publishing, copy paste URL into new webpage and download the file


# Process and Save Ticker Data Downloaded from Google Sheets Chunks
```{r}
setwd(file.path(Sys.getenv("USERPROFILE"),"Desktop","nasdaq googlesheet chunks 1995_01_01-2020_10_27"))

count = 1

# loop through each doc
for (j in 1:34) {

  print(j)
  # read donwloaded file from desktop
  path    = paste0("temp - temp ",j,".csv")
  all_dat = read.csv(path,sep=",",header=TRUE,stringsAsFactors=FALSE)
  
  # loop through every 6 columns and save to csv
  for (i in seq(1,ncol(all_dat),by=6)) {
    
    # extract data for 1 ticker
    temp = all_dat[2:nrow(all_dat),i:(i+5)]      # get relevant columns
    colnames(temp) = tolower(all_dat[1,i:(i+5)]) # define column names
    temp = temp[temp[,1]!="",]                   # remove NA rows
    
    # change format of dates
    col1 = unlist(strsplit(temp[,1]," "))[c(TRUE,FALSE)]
  
    if (!is.null(col1)) {
    
      # format columns
      if (j == 15 | j == 31) {
        temp[,1]   = as.Date(col1,format="%m/%d/%Y") # 
      } else {
        temp[,1]   = as.Date(col1,format="%d/%m/%Y") # as.Date(col1,format="%m/%d/%Y") #
      }
      temp[,2:6] = as.numeric(unlist(temp[,2:6]))
    
      # write to file
      write.csv(temp,paste0("nasdaq stocks/",df$Symbol[count],".csv"),row.names=FALSE)
      
      # if there is data for this ticker
      df$Data[count] = "Y"
      
    } else {
      
      # if there is no data for this ticker
      df$Data[count] = "N"
      
    }
    
    count = count + 1
      
  }

}

# Save NASDAQ Ticker Symbols and Info into Spreadsheet
write.csv(df,"NASDAQ.csv",row.names=FALSE)
```


-------------------------------------------------------------------------------------------------------
  Individual Stock Data
    
    https://finviz.com/quote.ashx?t=AACQ
-------------------------------------------------------------------------------------------------------


# Add Market Caps
```{r}
rm(list=ls())

# Load data
nasdaq = read.csv("NASDAQ.csv",sep=",",header=TRUE,stringsAsFactors=FALSE)
nasdaq = nasdaq[nasdaq$Data == "Y",]

# define new columns
nasdaq$Cap   = NA
nasdaq$Float = NA

# append new data to data frame
for (i in 1:nrow(nasdaq)) {
  
  print(i)
  
  # read webpage
  webpage = tryCatch({readLines(paste0("https://finviz.com/quote.ashx?t=",nasdaq$Symbol[i]))},
                      error   = function(cond) {return(NA)}
                     )
  
  if (!is.na(webpage)) {

    # market cap data
    line  = webpage[grepl("Market Cap",webpage)]
    start = gregexpr("<b>",line)[[1]][1]
    end   = gregexpr("</b>",line)[[1]][1]
    
    nasdaq$Cap[i] = substring(line,start+3,end-1)
    
    # float data in millions
    line  = webpage[grepl("Shs Float",webpage)]
    start = gregexpr("<b>",line)[[1]][1]
    end   = gregexpr("</b>",line)[[1]][1]
    
    nasdaq$Float[i] = substring(line,start+3,end-1)
    
  }

}

nasdaq[is.na(nasdaq)] = "-"

# change cap and float to millions
nasdaq$Cap   = as.numeric(substr(nasdaq$Cap,1,nchar(nasdaq$Cap)-1))     * ifelse(grepl("M",nasdaq$Cap),1,1000)
nasdaq$Float = as.numeric(substr(nasdaq$Float,1,nchar(nasdaq$Float)-1)) * ifelse(grepl("M",nasdaq$Float),1,1000)

# Save updated info
write.csv(nasdaq,"NASDAQ.csv",row.names=FALSE)
```
