
# Download Updated Data
```{r}
rm(list=ls())

# ------------------------------------------------------------------------------
# select start date
start_date = "DATE(2021,01,15)"
# ------------------------------------------------------------------------------

# function to download google spreadsheet ticker
googlefinance_single = function(ticker   = "NZ50G",
                                exchange = "NZE",
                                start    = start_date,
                                stop     = paste0("DATE(",gsub("-",",",Sys.Date()),")")) {
  return(
    paste0( "= GOOGLEFINANCE(\"" , exchange , ":" , ticker, "\",\"all\"," , start , "," , stop , ",\"DAILY\")" )
  )
}

# Load data
setwd(file.path(Sys.getenv("USERPROFILE"),"Desktop"))
nzx = list.files("nzx stocks")
nzx = gsub(".csv","",nzx)

# loop through tickers and generate excel formula
xlsx = c()
for (i in 1:length(nzx)) {
  
  # input with ticker and exchange symbols
  s = googlefinance_single(nzx[i], "NZE")

  # 6 column space between strings
  xlsx = c(xlsx,c(s,rep("",5)))

}

# get col names
xlsx_names = c()
for (i in 1:length(nzx)) {
  xlsx_names = c(xlsx_names, c(nzx[i],rep("",5)))
}

# write to output, default to desktop
xlsx           = data.frame(t(xlsx))
colnames(xlsx) = xlsx_names

write.csv(xlsx,file.path(Sys.getenv("USERPROFILE"),"Desktop","temp.csv"),row.names=FALSE)
```


# Manual Step for Downloading All Selected Ticker Data
1) Upload file generated in the code block above is uploaded onto google drive 
2) Converet file to a google sheet (formula will execute automatically)
3) Go to "File" -> "Publish to the Web" with type = ".csv", then click "Publish"
4) Using the link obtained from publishing, copy paste URL into new webpage and download the file


# Append Latest New Data
```{r}
# read downloaded file from desktop
setwd(file.path(Sys.getenv("USERPROFILE"),"Desktop"))
all_dat = read.csv(paste0("temp - temp.csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)

# loop through every 6 columns and save to csv
for (i in seq(1,ncol(all_dat),by=6)) {

  # current ticker processing
  edit_ticker = colnames(all_dat)[i]
  edit_ticker = gsub("[^A-Z]","",edit_ticker)
  print(edit_ticker)
  
  # extract data for 1 ticker
  temp = all_dat[2:nrow(all_dat),i:(i+5)]      # get relevant columns
  colnames(temp) = tolower(all_dat[1,i:(i+5)]) # define column names
  temp = temp[temp[,1]!="",]                   # remove NA rows
  
  # change format of dates
  col1 = unlist(strsplit(temp[,1]," "))[c(TRUE,FALSE)]

  # if there is data
  if (!is.null(col1)) {
  
    # format columns
    temp[,1]   = as.Date(col1,format="%d/%m/%Y") # as.Date(col1,format="%m/%d/%Y") # 
    temp[,1]   = as.character(temp[,1])
    temp[,2:6] = as.numeric(unlist(temp[,2:6]))
    
    # load stock
    edit_dat   = read.csv(paste0("nzx stocks/",edit_ticker,".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
    
    # only append if data is not there
    current_last_day  = as.Date(edit_dat$date[nrow(edit_dat)],format="%Y-%m-%d")
    updated_first_day = as.Date(temp$date[1],format="%Y-%m-%d")
    if (current_last_day < updated_first_day) {
      
      # append to stock
      write_dat  = rbind(edit_dat,temp)
      
      # append and write to file
      write.csv(write_dat,paste0("nzx stocks/",edit_ticker,".csv"),row.names=FALSE)
      
    }

  }
  
}
```
