
Findings, validate if MACD really crosses in 1 day problem:

- top 7 guarantees 99% chance of crossover in the next 1 day
- >50% in the top 7 has cross next day
- MACD diff value does not impact whether really cross or not
- For any most likely "N"th potential macd cross, there is ~25% there is no macd cross the next day


# Compute Stats For MACD Cross Over
```{r}
rm(list=ls())
source("Utils.R")

# set up stocks
nyse_stocks   = read.csv("NYSE.csv")
nasdaq_stocks = read.csv("NASDAQ.csv")
exchange      = c(rep("NYSE",nrow(nyse_stocks)),rep("NASDAQ",nrow(nasdaq_stocks)))

stocks = rbind(nyse_stocks[c("Symbol","Data","Cap","Float")],nasdaq_stocks[c("Symbol","Data","Cap","Float")])
stocks$exchange = exchange

# store values
macd_mat   = array(rep(NA,nrow(stocks)*8000*3),dim=c(nrow(stocks),8000,3))
small_data = c()

# read stock data
for (i in 1:nrow(stocks)) {
  
    print(stocks$Symbol[i])
  
    # check if stock data exists
    if (sum(paste0(stocks$Symbol[i],".csv") == 
        list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks")))) == 0) next
  
    # load stock
    path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks"))
    df   = read.csv(paste0(path,"/",stocks$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
    
    # skip if too short
    if (nrow(df) < 30) {
      small_data = c(small_data,stocks$Symbol[i])
      next
    }
    
    # compute ema and macd entries
    macd12_26_9 = macd(df$Close, 12, 26, 9)
    macd_cross  = crossover(macd12_26_9$signal,macd12_26_9$MACD) & macd12_26_9$MACD < 0
    
    # store values
    macd_mat[i, (8000 - length(macd_cross) + 1):8000,1] = macd_cross
    macd_mat[i, (8000 - length(macd_cross) + 1):8000,2] = macd12_26_9$signal
    macd_mat[i, (8000 - length(macd_cross) + 1):8000,3] = macd12_26_9$MACD

}

# compute difference in MACD line and signal line
MACD_diff = abs((macd_mat[,,2] - macd_mat[,,3])/macd_mat[,,3])
MACD_diff[macd_mat[,,2] >= 0] = NA
MACD_diff[macd_mat[,,3] >= 0] = NA
MACD_diff[macd_mat[,,2] <= macd_mat[,,3]] = NA
MACD_diff[!is.finite(MACD_diff)] = NA

# write data
#write.csv(macd_mat[,,1],file.path(Sys.getenv("USERPROFILE"),"Desktop","MACD_cross.csv"),row.names=FALSE)
write.csv(MACD_diff,file.path(Sys.getenv("USERPROFILE"),"Desktop","MACD_diff.csv"),row.names=FALSE)
```

# Proportion of Most Likely Crossovers with MACD Crossover in 1 Day
```{r}
# function to find if there is a cross in 1 day, given the n'th closest MACD cross
next_crosses = function(MACD_diff_matrix,n) {

  colind = unlist(apply(MACD_diff_matrix,2,function(x) {
                                                min_val = order(x,decreasing=FALSE)[n]
                                                out = ifelse(length(min_val)==0,NA,min_val)
                                                return(out)
                                           }
           ))
  
  crosses = sapply(1:(length(colind)-1),function(i) macd_mat[colind[i],i+1,1])
  return(crosses)
  
}

# initialize counters
crosses   = rep(0,dim(MACD_diff)[2]-1)
one_prob  = c()
prob_prob = c()
cum_prob  = c()

# iterate through the top i'th in terms of minimum MACD/signal values
for (i in 1:20) {
  
  crosses_temp = next_crosses(MACD_diff,i)
  crosses = crosses + crosses_temp
  
  # probability for single "i"
  one_prob = c(one_prob, sum(crosses_temp,na.rm=TRUE)/sum(!is.na(crosses_temp))*100)
  
  # probabilty given top "N", proportion of days actually contains MACD cross next day
  prob_prob = c(prob_prob, mean(crosses/i,na.rm=TRUE)*100)
  
  # probability for cumulative 1 to "i"th
  crosses_i = crosses >= 1
  cum_prob  = c(cum_prob, sum(crosses_i,na.rm=TRUE)/sum(!is.na(crosses_i))*100)
  
}

# find minimum macd diff for each day
colind = unlist(apply(MACD_diff,2,function(x) sort(x,decreasing=FALSE)[1]))

# macd diff for real crossovers
crossover_diff = MACD_diff[,1:7999][macd_mat[,2:8000,1]==1]

# setup subplots
par(mfcol=c(2,2))

# plot probabilities
plot(cum_prob,main="Proportion of Cross in 1 Day Given the Top N Most Likely Crosses",
     type="l",xlab="Top (N Most Likely)",ylab="Probability (%)",lwd=2,ylim=c(90,100))
points(cum_prob,lwd=2)
#lines(one_prob,col="grey",lwd=2)
abline(h=1:100,col=alpha("red",0.5),lty=2,lwd=1)
abline(v=1:i,col=alpha("orange",0.5),lty=2,lwd=1)

# plot barplot, given top N most probable cross over, how many actually produce crossover
names(prob_prob) = 1:20
barplot(prob_prob,main="Given Top N Most Likely Cross, How Many Actually Cross in 1 Day",
        xlab="Top (N Most Likely)",ylab="Probability (%)")
abline(h=50,col=alpha("red",0.5),lty=2,lwd=1)

# plot distribution of min values
hist(colind,breaks=seq(0,max(colind,na.rm=TRUE)+0.0001,by=0.0001),xlim=c(0,0.04),
     main="Distribution of MACD Diff Mostly Likely Before Cross",xlab="MACD Diff")
abline(v=quantile(colind,probs=c(50,75,90,95,99,99.9)/100,na.rm=TRUE),lty=2,col=alpha("red",0.5),lwd=2)
text(quantile(colind,probs=c(50,75,90,95,99,99.9)/100,na.rm=TRUE),700,
     labels=c("50%","75%","90%","95%","99%","99.9%"),cex=1,col="red")

# plot distribution of min values for actual crossovers
hist(crossover_diff,breaks=seq(0,max(crossover_diff,na.rm=TRUE)+0.01,by=0.01),xlim=c(0,1),
     main="Distribution of MACD Diff Before Real Cross",xlab="MACD Diff")
abline(v=quantile(crossover_diff,probs=c(50,75,90,95,99,99.9)/100,na.rm=TRUE),lty=2,col=alpha("red",0.5),lwd=2)
text(quantile(crossover_diff,probs=c(50,75,90,95,99,99.9)/100,na.rm=TRUE),50000,
     labels=c("50%","75%","90%","95%","99%","99.9%"),cex=1,col="red")
```

# Find Number of Most Likely MACD Enty that is False
```{r}
fake_macd_entry_finder = function(N,i) {
    
  # find index of minimum row (stock) for current column (time)  
  ind = order(MACD_diff[,i],decreasing=FALSE)[N]
  
  # check if stock data exists
  if (sum(paste0(stocks$Symbol[ind],".csv") == 
      list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[ind]," stocks")))) == 0) next

  # load stock
  path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[ind]," stocks"))
  df   = read.csv(paste0(path,"/",stocks$Symbol[ind],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
  
  # compute emas
  ema12 = ema(df$Close,12)
  ema26 = ema(df$Close,26)
  
  # Assign vals
  temp_high  = rep(NA,8000)
  temp_close = rep(NA,8000)
  temp_ema12 = rep(NA,8000)
  temp_ema26 = rep(NA,8000)
  
  temp_high[(8000 - nrow(df) + 1):8000]  = df$High
  temp_close[(8000 - nrow(df) + 1):8000] = df$Close
  temp_ema12[(8000 - nrow(df) + 1):8000] = ema12
  temp_ema26[(8000 - nrow(df) + 1):8000] = ema26
  
  # compute fake macd crossover signal
  price_entry = 351/28*(28/351* temp_close[i-1] + 11/13*(temp_ema12[i-2] - temp_ema12[i-1]) + 25/27*(temp_ema26[i-1] - temp_ema26[i-2]))
  
  return(list(iscross       = price_entry >= temp_close[i] & temp_high[i] > price_entry,
              macd_diff_val = MACD_diff[ind,i]))
  
}

# compute fake entries given top N
false_entry_cum = rep(0,dim(MACD_diff)[2]-2)
prop_fake_one   = c()
prob_fake_prob  = c()
prop_fake_cum   = c()

for (n in 1:20) {
  
  false_entry    = c()
  false_macd_val = c()
  
  # loop through all columns
  for (i in 3:dim(MACD_diff)[2]) {
    out = fake_macd_entry_finder(n,i)
    false_entry    = c(false_entry, out$iscross)
    false_macd_val = c(false_macd_val, out$macd_diff_val)
  }
  
  false_entry_cum = false_entry_cum + as.numeric(false_entry)
  
  # Given N'th potential cross, probability on average that it is fake entry signal
  prop_fake_one = c(prop_fake_one, sum(false_entry,na.rm=TRUE)/sum(!is.na(false_entry))*100)
  
  # Given top N potential crosses, proportion of days that contain fake entry signal
  prob_fake_prob = c(prob_fake_prob, mean(false_entry_cum/n,na.rm=TRUE)*100)
  
  # Given top 1 to N potential crosses, how many produce fake entry signal
  false_entry_cum_i = false_entry_cum >= 1
  prop_fake_cum     = c(prop_fake_cum, sum(false_entry_cum_i,na.rm=TRUE)/sum(!is.na(false_entry_cum_i))*100)
  
}

names(prop_fake_one)  = 1:20
names(prob_fake_prob) = 1:20
names(prop_fake_cum)  = 1:20

# produce plots
par(mfrow=c(1,3))

barplot(prop_fake_one,xlab="Top N (MACD Guesses)",ylab="Probability (%)",
        main="Probability That the N'th Guess is Fake Entry",ylim=c(0,50))
abline(h=seq(10,50,by=10),lty=2,col=alpha("red",0.5))
barplot(prob_fake_prob,xlab="Top N (MACD Guesses)",ylab="Probability (%)",
        main="Proportion of Days Containing Fake Entry for the Top N Guesses",ylim=c(0,50))
abline(h=seq(10,50,by=10),lty=2,col=alpha("red",0.5))
barplot(prop_fake_cum,xlab="Top N (MACD Guesses)",ylab="Probability (%)",
        main="Probability That there is a Fake Entry in the Top N Guesses",ylim=c(0,100))
abline(h=seq(10,100,by=10),lty=2,col=alpha("red",0.5))
```

