
# Initialization
```{r}
rm(list=ls())
source("Utils.R")

# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
# MACD Strategy
# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
macd_strategy = function(dat_i) {
  
  # empty data.frame to return in case of errors
  empty_out = data.frame(entry.date=as.Date(NA),exit.date=as.Date(NA),outcome=NA)
  
  # return if data is less than 200 in length and cant compute 200ema
  if (nrow(dat_i) <= 200) return(empty_out)

  # techinicals
  ema200      = ema(dat_i$close, 200)
  macd12_26_9 = macd(dat_i$close, 12, 26, 9)
  
  # entry
  macd_cross  = crossover(macd12_26_9$signal,macd12_26_9$MACD)
  
  # entry signals, using ema filter improves nyse but not for nasdaq
  macd_entry = which(macd_cross & macd12_26_9$MACD < 0 & dat_i$close > ema200)

  # loop through macd entries, how to find prior swing low, use that as stop loss, and take profit is 1.5x greater
  out_date_entry = as.Date(c())
  out_date_exit  = as.Date(c())
  out_return     = as.numeric(c())
  
  for (m in macd_entry) {
    
    # get local region of current price/date
    price     = dat_i$close[max(c((m - 100),1)):m]
    price_low = dat_i$low[max(c((m - 100),1)):m]
    date      = dat_i$date[max(c((m - 100),1)):m]
    
    # compute prior swing low
    price_smooth = smooth(c(price, price[length(price)]*seq(1.01,by=0.01,length=50)),0.1)[1:length(price)]
    minimas      = local_extrema(price_smooth,max=FALSE)
    min_ind      = minimas[length(minimas)]
    min_date     = date[min_ind]
    
    # find minimum in local region of min_date
    min_date = date[which.min(price_low[max(c(1,(min_ind - 5))):min(c(length(price_low),(min_ind + 5)))]) + min_ind - 6]
    
    # set up bracket trade: entry and stop loss and exit
    price_entry  = dat_i$close[m]
    price_stop   = dat_i$low[dat_i$date == min_date]*0.995 # put stop loss %0.5 below prior swing low
    
    # if stop is near ema200, then use ema200 as stop loss as it is stronger support
    #if (ema200[m] < price_entry & ema200[m] > price_stop) price_stop = ema200[m]
    
    price_profit = dat_i$close[m] * (1 + (price_entry - price_stop)/price_entry * 1.5) # 1R : 1.5R
    
    # skip if stop loss is too large (take profit is higher than 7.5%)
    # skip if price has already moved by over 5% in favor of the trade before the entry ()
    crit1 = abs(price_stop - price_entry)/price_entry*100 > 5
    crit2 = (dat_i$close[m] - dat_i$close[m-3])/dat_i$close[m]*100 > 2.5
    if (ifelse(is.na(crit1),FALSE,crit1)) next
    if (ifelse(is.na(crit2),FALSE,crit2)) next
    
    # find which price is hit first
    ind_stop = which(dat_i$low[m:nrow(dat_i)] <= price_stop)[1] + m - 1
    ind_exit = which(dat_i$high[m:nrow(dat_i)] >= price_profit)[1] + m - 1
    
    outcome   = which.min(c(ind_stop,ind_exit))
    exit_date = min(c(ind_stop,ind_exit),na.rm=TRUE)
    
     # store the trade if there is an exit, and if the exit date is not in the future
    if (is.finite(exit_date) & !is.na(dat_i$date[exit_date])) {
      
      # set dates
      date_entry = dat_i$date[m] # enter at next candle
      date_stop  = min_date
      date_exit  = dat_i$date[exit_date]
      
      # compute profits/loss
      return = ifelse(outcome==1,-1,1.5)
  
      # save data
      out_date_entry = c(out_date_entry,date_entry)
      out_date_exit  = c(out_date_exit,date_exit)
      out_return     = c(out_return, return)
      
    }
    
  }
  
  # output data frame with all trades
  dat_out = data.frame(entry.date = as.Date(out_date_entry),
                       exit.date  = as.Date(out_date_exit),
                       outcome    = as.numeric(out_return))
  
  # if no trades return empty matrix
  if (nrow(dat_out)==0) {
    return(empty_out)
  } else {
    return(dat_out)
  }
  
}
```

# Load and Run MACD strategy
```{r}
exchange = "nyse"

# set up stocks
stocks = read.csv(paste0(toupper(exchange),".csv"))
stocks$macd_return = NA
stocks$macd_n      = NA
stocks$gradient    = NA
stocks$residual    = NA

# dataframe containing history of all trades
trade_hist = data.frame(ticker=character(),entry.date=as.Date(character()),exit.date=as.Date(character()),outcome=numeric())

# read stock data
for (i in 1:nrow(stocks)) {
  
    print(stocks$Symbol[i])
  
    # load stock
    path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(exchange," stocks"))
    df   = read.csv(paste0(path,"/",stocks$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
    
    # run strategies
    macd_out = macd_strategy(df)
    
    # appending trade history
    trade_hist = rbind(trade_hist, cbind(ticker=stocks$Symbol[i],macd_out))
    
    # save winning percentages and number of trades
    macd_out = macd_out[!is.na(macd_out$entry.date),] # remove NA rows
    
    stocks$macd_return[i] = sum(macd_out$outcome>0)/nrow(macd_out)
    stocks$macd_n[i]      = nrow(macd_out)
    
    # compute linear regression
    LR = lm(1:nrow(df) ~ df$close)
    
    stocks$gradient[i] = LR$coefficients[2]
    stocks$residual[i] = mean(LR$residuals^2)
    
}

# compute win rate and average position length
trade_hist   = trade_hist[!is.na(trade_hist$outcome),]
win_lose_seq = trade_hist$outcome[order(trade_hist$entry.date)]
rle          = rle(win_lose_seq)

sprintf("Win Rate: %.1f%%", sum(trade_hist$outcome>0)/nrow(trade_hist)*100)
sprintf("Average Hold Length: %.0f days", mean(trade_hist$exit.date-trade_hist$entry.date))

# write to output
if (TRUE) { # TRUE FALSE
  write.csv(stocks,paste0(exchange,"_macd_returns.csv"),row.names=FALSE)
  write.csv(trade_hist,paste0(exchange,"_macd_history.csv"),row.names=FALSE)
}

# BEST:
# NASDAQ - 44.4%
# NYSE   - 44.9%
```

# Compute Return with Non-Overlapping Trades (Realistic Metrics)
```{r}
# sort data
trade_hist = trade_hist[order(trade_hist$entry.date),]

# initialize counters
rm_rows = c()
last_exit = trade_hist$exit.date[1]

# loop through all data
for (i in 1:nrow(trade_hist)) {
  
  if (trade_hist$entry.date[i] < last_exit) {
    rm_rows = c(rm_rows,i)
  } else {
    last_exit = trade_hist$exit.date[i]
  }
  
}

# filter out the removed rows
trade_hist = trade_hist[-rm_rows,]

# summarize statistics
rle = rle(trade_hist$outcome)

sprintf("Win Streak: %i",        max(rle$lengths[rle$values==1.5],na.rm=TRUE))
sprintf("Lose Streak: %i",       max(rle$lengths[rle$values==-1],na.rm=TRUE))
sprintf("Win Rate: %.1f%%",      sum(trade_hist$outcome>0)/nrow(trade_hist)*100)
sprintf("Trades Per Year: %.1f", nrow(trade_hist)/as.numeric((trade_hist$exit.date[nrow(trade_hist)] - trade_hist$entry.date[1])/365.25))
sprintf("Average Hold Length: %.0f days", mean(trade_hist$exit.date-trade_hist$entry.date))
sprintf("Cumulative Returns: %0.1f%%",    tail(cumprod(c(1,1+trade_hist$outcome/100))-1,1)*100)

# project return
macd_trade = cumprod(c(1,1+trade_hist$outcome/100))[-1]
plot(as.Date(sort(trade_hist$entry.date)),macd_trade,type="l",log="y")
abline(h=10^(-2:100),col=alpha("grey",0.5))
```

# Further Filtering Based on Results
```{r}
# load returns
stocks = read.csv(paste0(exchange,"_macd_returns.csv"),sep=",")
hist   = read.csv(paste0(exchange,"_macd_history.csv"),sep=",")

# # compute additional metrics
# for (i in 1:nrow(stocks)) {
# 
#   print(stocks$Symbol[i])
#   
#   # load data
#   path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(exchange," stocks"))
#   df   = read.csv(paste0(path,"/",stocks$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
#   
# }

# filterS
returns = stocks[!is.na(stocks$Cap) & stocks$macd_n != 0,]
returns = returns[returns$Cap>10000,] # only take large caps
#returns = returns[returns$gradient>0,]
#returns = returns[returns$residual<750000,]

# compute summaries
s1 = sum(returns$macd_n)/25
s2 = sum(returns$macd_return * returns$macd_n / sum(returns$macd_n)) * 100

sprintf("Average Number of Trades Per Year: %0.f, with Winning Percentage: %0.1f%%",s1,s2)
```

- dont take trades when price is in a range, when 200 ema is flat, and price action crosses above and below ema several times
- use prior pullbacks as support, and longer time-frame areas as support, and avoid buying near long-term resistance

- trailing stop loss
- test if 200ema filter is needed or not at the very end