
# How To Use
# -----------------------------------------------------------------------------------------------
# - run code to find most likely crosses
# - manually select with ones seem the most likely to cross
# - set up trades on IBKR with defined entry price
# # 
# - after 1st day, see which trades got executed
# - recalculate the stop loss % using the low of the 1st day if it is lower than prior stop loss
# - add the stop loss using 1st day's high, repeat everyday until position closes
# -----------------------------------------------------------------------------------------------

# Find Next Trade
```{r}
rm(list=ls())
source("Utils.R")

# set up stock paths
nyse_stocks   = read.csv("nyse.csv")
nasdaq_stocks = read.csv("nasdaq.csv")
exchange      = c(rep("nyse",nrow(nyse_stocks)),rep("nasdaq",nrow(nasdaq_stocks)))

stocks = rbind(nyse_stocks[c("Symbol","Cap","Float")],nasdaq_stocks[c("Symbol","Cap","Float")])

# load stocks database
stocks$exchange    = exchange
stocks$diff.MACD   = NA
stocks$price.entry = NA
stocks$stop.per    = NA

# get list of tickers
for (i in 1:length(stocks$Symbol)) {
  
  print(stocks$Symbol[i])

  # check if stock data exists
  if (sum(paste0(stocks$Symbol[i],".csv") == 
      list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks")))) == 0) next

  # load stock
  path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks"))
  df   = read.csv(paste0(path,"/",stocks$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
  
  # return if data is less than 35 in length and cant compute MACD
  if (nrow(df) <= 35) next

  # techinicals
  ema12       = ema(df$Close,  12)
  ema26       = ema(df$Close,  26)
  macd12_26_9 = macd(df$Close, 12, 26, 9)
  
  # skip trade if MACD is above signal line, or if either line is above 0
  macd_n = tail(macd12_26_9$MACD,1)
  sig_n  = tail(macd12_26_9$signal,1)
  if (macd_n > sig_n | sig_n  >= 0 | macd_n >= 0) next
  diffnorm = abs((sig_n - macd_n)/sig_n)
  
  # # # # # analyze price action at latest price (start of strategy code)
  m = nrow(df) # entry is m+1 in this case
  
  # get local region of current price/date
  price     = df$Close[max(c((m - 100),1)):m]
  price_low = df$Low[max(c((m - 100),1)):m]
  date      = df$Date[max(c((m - 100),1)):m]
  
  # compute prior swing low
  price_smooth = smooth(c(price,price[length(price)]*seq(1.01,by=0.01,length=50)),0.1)[1:length(price)]
  minimas      = local_extrema(price_smooth,max=FALSE)
  min_ind      = minimas[length(minimas)]
  min_date     = date[min_ind]
  
  # find minimum in local region of min_date
  min_date = date[which.min(price_low[max(c(1,(min_ind - 5))):min(c(length(price_low),(min_ind + 5)))]) + min_ind - 6]
  
  # derive the exact price of crossover, and thus, entry price
  price_entry = 351/28*(28/351*df$Close[m] + 11/13*(ema12[m-1] - ema12[m]) + 25/27*(ema26[m] - ema26[m-1]))
  
  # set stop price and stop loss percentage
  price_stop = df$Low[df$Date == min_date][1] # Use Low or Close
  stop_per   = (price_stop - price_entry)/price_entry*100
  
  # skip if stop loss is too large, or if its positive which means the code fked up
  if (stop_per < -2 | stop_per > 0) next
 
  # save values
  stocks$diff.MACD[i]   = diffnorm
  stocks$price.entry[i] = price_entry
  stocks$stop.per[i]    = stop_per
  
}

# Filter Stocks
stocks_enter = stocks
stocks_enter = stocks_enter[stocks_enter$Cap > 2000,]
stocks_enter = stocks_enter[!is.na(stocks_enter$diffMACD),]
stocks_enter = stocks_enter[order(stocks_enter$diffMACD,decreasing=FALSE),]
rownames(stocks_enter) = NULL

# Save Potential Entries
write.csv(stocks_enter,file.path(Sys.getenv("USERPROFILE"),"Desktop",
                                 paste0("Next Trades",as.character(Sys.Date()),".csv")),row.names=FALSE)
```

# Plot Stocks
```{r}
dir.create(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0("Next Trades",as.character(Sys.Date()))))

for (i in 1:nrow(stocks_enter)) {

  # load stock
  path    = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks_enter$exchange[i]," stocks"))
  df      = read.csv(paste0(path,"/",stocks_enter$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
  df$date = as.Date(df$date)
    
  # compute macd
  ema200 = ema(df$close,200)
  macd12_26_9 = macd(df$close, 12, 26, 9)
  
  # crop df
  r                  = 22
  ema200             = ema200[(nrow(df) - r):nrow(df)]
  macd12_26_9$MACD   = macd12_26_9$MACD[(nrow(df) - r):nrow(df)]
  macd12_26_9$signal = macd12_26_9$signal[(nrow(df) - r):nrow(df)]
  df                 = df[(nrow(df) - r):nrow(df),]
  
  # save
  savepath = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0("Next Trades",as.character(Sys.Date())))
  plot_stock(df,sub="macd",
             emas=list(ema200),macd=macd12_26_9,
             save=TRUE,savename=paste0(savepath,"/",i,"_",stocks_enter$exchange[i],"-",stocks_enter$Symbol[i]))

}
```
