
# -----------------------------------------------------------------------------------------------
# How To Use
# -----------------------------------------------------------------------------------------------
# - run code to find most likely crosses
# - manually select tickers with clean MACD convergence patterns
# - set up trades on IBKR with defined entry price using limit order at the open
# # 
# - after 1st day, see which trades got executed
# - recalculate the stop loss % using the low of the 1st day if it is lower than prior stop loss
# - add the stop loss order using 1st day's high, repeat everyday until position closes
# -----------------------------------------------------------------------------------------------

# Find Next Trade
```{r}
# setwd("C:/Users/zxio506/OneDrive/Assets/Securities/Trading Stocks")

rm(list=ls())
source("Utils.R")

# set up stock paths
nyse_stocks   = read.csv("nyse.csv")
nasdaq_stocks = read.csv("nasdaq.csv")
exchange      = c(rep("nyse",nrow(nyse_stocks)),rep("nasdaq",nrow(nasdaq_stocks)))

stocks = rbind(nyse_stocks[c("Symbol","Cap","Float")],nasdaq_stocks[c("Symbol","Cap","Float")])

# load stocks database
stocks$exchange    = exchange
stocks$diff.MACD   = NA
stocks$price.entry = NA
stocks$stop.loss   = NA
stocks$stop.per    = NA

# get list of tickers
for (i in 1:length(stocks$Symbol)) {
  
  print(stocks$Symbol[i])

  # check if stock data exists
  if (sum(paste0(stocks$Symbol[i],".csv") == 
      list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks")))) == 0) next

  # load stock
  path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(stocks$exchange[i]," stocks"))
  df   = read.csv(paste0(path,"/",stocks$Symbol[i],".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)
  df   = df[!is.na(df$Close),]
  
  # return if data is less than 35 in length and cant compute MACD
  if (nrow(df) <= 35) next

  # techinicals
  ema12       = ema(df$Close,  12)
  ema26       = ema(df$Close,  26)
  macd12_26_9 = macd(df$Close, 12, 26, 9)
  
  # skip trade if MACD is above signal line, or if either line is above 0
  macd_n = tail(macd12_26_9$MACD,1)
  sig_n  = tail(macd12_26_9$signal,1)
  if (macd_n > sig_n | sig_n  >= 0 | macd_n >= 0) next
  diffnorm = abs((sig_n - macd_n)/sig_n)
  
  # # # # # analyze price action at latest price (start of strategy code)
  m = nrow(df) # entry is m+1 in this case
  
  # get local region of current price/date
  price     = df$Close[max(c((m - 100),1)):m]
  price_low = df$Low[max(c((m - 100),1)):m]
  date      = df$Date[max(c((m - 100),1)):m]
  
  # compute prior swing low
  price_smooth = smooth(c(price,price[length(price)]*seq(1.01,by=0.01,length=50)),0.1)[1:length(price)]
  minimas      = local_extrema(price_smooth,max=FALSE)
  min_ind      = minimas[length(minimas)]
  
  # find minimum in local region of min_date
  min_date = date[which.min(price_low[max(c(1,(min_ind - 5))):min(c(length(price_low),(min_ind + 5)))]) + min_ind - 6]
  
  # derive the exact price of crossover, and thus, entry price
  price_entry = (macd12_26_9$signal[m] - 11/13*ema12[m] + 25/27*ema26[m])/(2/13 - 2/27)
  
  # set stop price and stop loss percentage
  price_stop = df$Low[df$Date == min_date][1] # Use Low or Close
  stop_per   = (price_stop - price_entry)/price_entry*100
  
  # skip if stop loss is too large, or if its positive which means the code fked up
  if (stop_per < -2 | stop_per > 0) next
 
  # save values
  stocks$diff.MACD[i]   = diffnorm
  stocks$price.entry[i] = price_entry
  stocks$stop.loss[i]   = price_stop
  stocks$stop.per[i]    = stop_per
  
}

# Filter Stocks
stocks_enter = stocks
stocks_enter = stocks_enter[stocks_enter$Cap > 1000,]
stocks_enter = stocks_enter[!is.na(stocks_enter$diff.MACD),]
stocks_enter = stocks_enter[order(stocks_enter$diff.MACD,decreasing=FALSE),]
rownames(stocks_enter) = NULL

# Reformat dataframe
stocks_enter$price.entry = round(stocks_enter$price.entry,2)
stocks_enter$stop.loss   = round(stocks_enter$stop.loss,2)

# Save Potential Entries
stocks_enter = stocks_enter[1:min(20,nrow(stocks_enter)),c("Symbol","exchange","Cap","Float","price.entry","stop.loss","stop.per")]

write.csv(stocks_enter,paste0("Next Trades ",as.character(Sys.Date()),".csv"),row.names=FALSE)
```

# Recompute Stop % After 1st Day
```{r}
ticker   = "TAK"
exchange = "NYSE" # NYSE NASDAQ

# check if stock data exists
if (sum(paste0(ticker,".csv") == 
    list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(exchange," stocks")))) == 0) next

# load stock
path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(ticker," stocks"))
df   = read.csv(paste0(path,"/",ticker,".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)

# get lastest value of data
m = nrow(df) # entry is m+1 in this case

# get local region of current price/date
price     = df$Close[max(c((m - 100),1)):m]
price_low = df$Low[max(c((m - 100),1)):m]
date      = df$Date[max(c((m - 100),1)):m]

# compute prior swing low
price_smooth = smooth(c(price,price[length(price)]*seq(1.01,by=0.01,length=50)),0.1)[1:length(price)]
minimas      = local_extrema(price_smooth,max=FALSE)
min_ind      = minimas[length(minimas)]
min_date     = date[min_ind]

# find minimum in local region of min_date
min_date = date[which.min(price_low[max(c(1,(min_ind - 5))):min(c(length(price_low),(min_ind + 5)))]) + min_ind - 6]

# set stop price and stop loss percentage
price_stop = df$Low[df$Date == min_date][1] # Use Low or Close
stop_per   = (price_stop - price_entry)/price_entry*100

# display outputs
sprintf("Stop Price = %0.2f",price_stop)
sprintf("Stop Percentage = %0.9f",stop_per)
```

# MACD Cross Tester
```{r}
ticker   = "TAK"
exchange = "NYSE" # NYSE NASDAQ

# check if stock data exists
if (sum(paste0(ticker,".csv") == 
    list.files(file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(exchange," stocks")))) == 0) next

# load stock
path = file.path(Sys.getenv("USERPROFILE"),"Desktop",paste0(exchange," stocks"))
df   = read.csv(paste0(path,"/",ticker,".csv"),sep=",",header=TRUE,stringsAsFactors=FALSE)

# get lastest value of data
m = nrow(df)

ema12       = ema(df$Close,  12)
ema26       = ema(df$Close,  26)
macd12_26_9 = macd(df$Close, 12, 26, 9)
price_entry = (macd12_26_9$signal[m] - 11/13*ema12[m] + 25/27*ema26[m])/(2/13 - 2/27)

macd12_26_9 = macd(c(df$Close,price_entry), 12, 26, 9)

price_entry
tail(macd12_26_9$MACD)
tail(macd12_26_9$signal)
```

