
--------------------------------
Round Trip Comission %
--------------------------------
Order Amount | Sharsies | ASB
--------------------------------
1000	         1.00	      6.00
2000	         1.00	      3.00
3000	         1.00	      2.00
4000  	       0.80	      1.50
5000  	       0.68	      1.20
6000	         0.60	      1.00
7000	         0.54	      0.86
8000	         0.50	      0.75
9000         	 0.47	      0.67
10000	         0.44	      0.60
20000          0.32	      0.60
30000	         0.28	      0.60
40000	         0.26	      0.60
50000	         0.25	      0.60
100000         0.22	      0.60
--------------------------------

--------------------------------------------------------------------------------------------------------------------------------
Strategy Execution
--------------------------------------------------------------------------------------------------------------------------------
  - check holidays, if there has been in US/UK/NZ, fill the date with prior day's values (line 184)
  - check missing values

Entry:
  - Entry limit is the exact price of crossover
  - Lower entry is preferred as it results in higher crossover and more profit
  - Enter with limit order near trading day close, limit set below cross value
  - If there are multiple entries, trade the ETF with the best winning %

Exit:
  - Exit limit is the exact price of crossunder
  - Higher exit is preferred as it results in lower crossunder and more profit
  - Exit with limit order near trading day close, limit set above cross value

--------------------------------------------------------------------------------------------------------------------------------

# 0) Initialize Functions and Load Ticker List
```{r}
rm(list=ls())

# load etf pairs information
etf = read.csv("ETFpairs_sorted.csv",header=TRUE)

# preprocess some info
etf$min_date = as.Date(etf$min_date,format="%m/%d/%Y")

# rolling cumulative return moving average
rcma = function(x,n) {
  
  n     = n - 1
  rma_x = (x[1:n]-x[1])/x[1]

  for (i in seq(1, length(x)-n)) {
    rma_x = c(rma_x, (x[i+n]-x[i])/x[i])
  }
  
  return(rma_x*100)
  
}

# compute location of cross over
crossover = function(x1,x2) {
  
  # find max time steps
  l = max(c(length(x1),length(x2)))
  
  # duplicate values if only singular numeric value is provided
  if (length(x1) == 1) x1 = rep(x1,l)
  if (length(x2) == 1) x2 = rep(x2,l)
  
  # find which indices are true, if NA then set as false. x1 was more, now is less
  cross_ind = c(FALSE,x1[1:(l-1)] > x2[1:(l-1)] & x1[2:l] < x2[2:l])
  cross_ind[is.na(cross_ind)] = FALSE
  
  return(cross_ind)
  
}

# plot ticker
plot_etf = function(data,data_ref,data_diff,data_fx,
                    ind_entry,ind_exit,
                    save=FALSE,savename="") {
  
  # save plot
  if (save) png(paste0(savename,".png"), width = 500, height = 750)
  
  # set up plot area
  layout(matrix(1:2,2,1),heights=c(1.5,1))
  
  # set up plot range
  xrange = range(data$date,na.rm=TRUE)
  yrange = range(c(data$high*1.005,data$low*0.995,data_ref),na.rm=TRUE)
  
  # initialize plot with margin sizes
  par(mar=c(1,4,1,1))
  plot(-999,-999,xlim=xrange,ylim=yrange,xlab="",ylab="Price (NZD)",xaxt="n",yaxt="n")
  
  # label axis
  axis(2,at=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),
       labels=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),las=2)
  
  # reference index price
  lines(data$date,data_ref,col="orange")
  points(data$date,data_ref,col="orange",pch=20)
  
  # insert candlesticks
  abline(v=data$date,col="grey80",lty=4)
  colors = ifelse(data$close >= data$open,"forestgreen","tomato")
  segments(x0  = data$date, y0 = data$low
          ,x1  = data$date, y1 = data$high
          ,col = colors, lwd=1
  )
  rect(xleft   = data$date-0.3
      ,ybottom = ifelse(data$close >= data$open,data$open,data$close)
      ,xright  = data$date+0.3
      ,ytop    = ifelse(data$close >= data$open,data$close,data$open)
      ,col     = colors,border=colors
  )
  
  # plot entry and exit
  points(data$date[ind_entry],data$low[ind_entry]*0.995,col="blue",pch=24,cex=2,lwd=3)
  points(data$date[ind_exit],data$high[ind_exit]*1.005,col="blue",pch=25,cex=2,lwd=3)
  
  # set up plot range
  yrange2 = range(c(data_diff,data_fx),na.rm=TRUE)
  
  # initialize plot with margin sizes
  par(mar=c(6,4,0,1))
  plot(-999,-999,xlim=xrange,ylim=yrange2,xlab="",ylab= "Index - NZ ETF",xaxt="n",las=1)
  
  # label axis
  axis(1,at=seq(xrange[1],xrange[2],by=1),labels=seq(xrange[1],xrange[2],by=1),las=2)
  
  # add diff plot
  abline(h=-10:10,col="grey80",lty=4)
  abline(v=data$date,col="grey80",lty=4)
  abline(h=c(1.5,-1.0),col="deepskyblue",lty=2,lwd=2)
  
  lines(data$date,data_diff,col="black")
  points(data$date,data_diff,col="black",pch=20)
  
  lines(data$date,data_fx,col="red")
  points(data$date,data_fx,col="red",pch=20)
  
  # save plot
  if (save) dev.off()
  
}
```

# 1) Back Test Strategy On All Data
```{r}
# store data
out_ticker      = c()
out_exchange    = c()
out_ind_entry   = c()
out_ind_exit    = c()
out_date_entry  = c()
out_date_exit   = c()
out_price_entry = c()
out_price_exit  = c()
out_return      = c()

# loop through every ETF pair
for (n in 1:nrow(etf)) {
  
  # load data
  etf_NZ = read.csv(paste0("data/",etf$ETF[n],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  etf_id = read.csv(paste0("data/",etf$Index[n],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")

  etf_NZ$date = as.Date(etf_NZ$date)
  etf_id$date = as.Date(etf_id$date)
  
  # adjust nz etf and index dates, with preset min-date
  etf_NZ = etf_NZ[etf_NZ$date >= etf$min_date[n],]

  # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
  # adjust if recent holidays caused a day mismatch: for US/UK and NZ
  if (etf$Exchange[n] == "NYSEARCA") {
      if (FALSE) { # TRUE FALSE
        holiday       = as.Date("2021-09-06") # date to interpolate and insert
        temp_row      = tail(etf_id[etf_id$date <= holiday,],1)
        temp_row$date = holiday
        etf_id        = rbind(etf_id,temp_row)
        etf_id        = etf_id[order(etf_id$date),]
      }
  } else if (etf$Exchange[n] == "LON") {
      if (FALSE) { # TRUE FALSE
        holiday       = as.Date("2021-08-30") # date to interpolate and insert
        temp_row      = tail(etf_id[etf_id$date <= holiday,],1)
        temp_row$date = holiday
        etf_id        = rbind(etf_id,temp_row)
        etf_id        = etf_id[order(etf_id$date),]
      }
  } 
  
  if (FALSE) { #NZ
    holiday       = as.Date("2021-08-30") # date to interpolate and insert
    temp_row      = tail(etf_id[etf_id$date <= holiday,],1)
    temp_row$date = holiday
    etf_id        = rbind(etf_id,temp_row)
    etf_id        = etf_id[order(etf_id$date),]
  }
  # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
  
  # adjust for different date/time zones in US/UK vs NZ, dont use last date for index depending on time
  if (etf$Exchange[n] != "ASX") etf_id$date = etf_id$date + 1
  etf_id = etf_id[(nrow(etf_id)-nrow(etf_NZ)+1):nrow(etf_id),]        # if downloaded during NZX hours
  #etf_id = etf_id[(nrow(etf_id)-nrow(etf_NZ)+1-1):(nrow(etf_id)-1),] # if downloaded before NZX opens
  
  # get currency data
  if (etf$Exchange[n] == "NYSEARCA") {
    fx = read.csv(paste0("data/NZDUSD.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  } else if (etf$Exchange[n] == "LON") {
    fx = read.csv(paste0("data/NZDGBP.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  } else if (etf$Exchange[n] == "ASX") {
    fx = read.csv(paste0("data/NZDAUD.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  }
  fx$date = as.Date(fx$date)
  
  # compute cumulative prices
  rn       = 5
  cum_nz   = rcma(etf_NZ$close,rn)
  cum_id   = rcma(etf_id$close,rn)
  cum_diff = cum_id - cum_nz
  cum_fx   = rcma(fx$close,rn)
  
  # higher filter
  rn2       = 22
  cum_nz2   = rcma(etf_NZ$close,rn2)
  cum_id2   = rcma(etf_id$close,rn2)
  cum_diff2 = cum_id2 - cum_nz2
  
  # entry indices
  #ind = which(crossover(1.5,cum_diff))
  ind = which(crossover(1.5,cum_diff) & cum_diff2 > 0.5)                  # ********** TUNENABLE x2
  
  # loop through every trade and apply strategy
  for (i in ind) {
    
    # set entry price
    price_entry = etf_NZ$close[i]
    
    # exit criteria
    ind_exit = crossover(cum_diff[i:length(cum_diff)],-1.0)             # ********** TUNENABLE
    ind_exit = which(ind_exit)[1] + i - 1

    # if no exit then skip trade
    if (is.na(ind_exit)) next
    
    # only hold for a max period of time before exiting
    #if ((ind_exit-i) > 10) ind_exit = i + 10

    # compute exit price
    price_exit = etf_NZ$close[ind_exit]
    
    # compute return
    return = (price_exit - price_entry)/price_entry*100
    
    # store outputs
    out_ticker      = c(out_ticker,      etf$ETF[n])
    out_exchange    = c(out_exchange,    etf$Exchange[n])
    out_ind_entry   = c(out_ind_entry,   i)
    out_ind_exit    = c(out_ind_exit,    ind_exit)
    out_date_entry  = c(out_date_entry,  as.character(etf_NZ$date[i]))
    out_date_exit   = c(out_date_exit,   as.character(etf_NZ$date[ind_exit]))
    out_price_entry = c(out_price_entry, price_entry)
    out_price_exit  = c(out_price_exit,  price_exit)
    out_return      = c(out_return,      return)
    
  }
  
}

# store all trades
out = data.frame(ticker      = out_ticker,
                 exchange    = out_exchange,
                 ind.entry   = out_ind_entry,
                 ind.exit    = out_ind_exit,
                 date.entry  = as.Date(out_date_entry),
                 date.exit   = as.Date(out_date_exit),
                 price.entry = out_price_entry,
                 price.exit  = out_price_exit,
                 return      = out_return)

# apply comission
out$return = out$return - 0.5
out = out[!is.na(out$return),]
out$outcome = ifelse(out$return > 0, TRUE, FALSE)

# Summarize
ls = list()
ls[[1]] = sprintf("---------------------------")
ls[[2]] = sprintf("Avg Win:  %0.2f%%", mean(out$return[out$outcome]))
ls[[3]] = sprintf("Avg Loss: %0.2f%%", mean(out$return[!out$outcome]))
ls[[4]] = sprintf("Win Rate: %0.1f%%", sum(out$outcome)/nrow(out)*100)
ls[[5]] = sprintf("Expected: %0.2f%%", sum(out$outcome)*mean(out$return[out$outcome])/nrow(out) + 
                                           sum(!out$outcome)*mean(out$return[!out$outcome])/nrow(out))
ls[[6]] = sprintf("Avg Hold Period: %0.1f Days", mean(out$ind.exit-out$ind.entry))
cat(paste0(ls,collapse="\n"))

# Summarize Tickers By Individual Win Rates
# temp = aggregate(out[,c(9,10)], by = list(out$ticker,out$exchange), FUN = mean)
# temp = temp[order(temp$Group.1),]
# temp$n = table(out$ticker)
# View(temp)

aggregate(out[,c(9,10)], by = list(out$exchange), FUN = mean)
```

# 2) Simulate Portfolio, Multiple Positions
```{r}
# sort by date and define new dataframe, with coutners
out2          = out[order(out$date.entry),]
out2$real     = FALSE
out2$active   = FALSE
out2$n_active = NA
max_active    = 1

for (i in 1:nrow(out2)) {

  # exit previous positions which has passed
  out2$active[out2$date.entry[i] > out2$date.exit] = FALSE
  
  # if there are still position slots available
  if (sum(out2$active) < max_active) {
    out2$active[i] = TRUE
    out2$real[i]   = TRUE
  }

  out2$n_active[i] = sum(out2$active)
  
}

# filter trades executed, and adjust return per trade due to position sizing
out2 = out2[out2$real,]
out2$return = out2$return/max_active

# plot portfolio performance
plot(out2$date.entry,cumprod(out2$return/100+1),type="l",log="y")
abline(h=1:10*0.5,lty=2, col="grey25")
abline(v=as.Date(paste0(2018:2025,"-01-01")),lty=2, col="grey25")
lines(out2$date.entry,cumprod(out2$return/100+1),col="blue",lwd=2)
points(out2$date.entry,cumprod(out2$return/100+1),col="black",pch=21)

# Summarize
ls = list()
ls[[1]] = sprintf("---------------------------")
ls[[2]] = sprintf("Win Rate: %0.1f%%",           sum(out2$outcome)/nrow(out2)*100)
ls[[3]] = sprintf("Expected: %0.2f%%",           sum(out2$outcome)*mean(out2$return[out2$outcome])/nrow(out2) + 
                                                   sum(!out2$outcome)*mean(out2$return[!out2$outcome])/nrow(out2))
ls[[4]] = sprintf("Avg Hold Period: %0.1f Days", mean(out2$ind.exit-out2$ind.entry))
ls[[5]] = sprintf("Trades Per Year: %0.0f",      sum(out2$date.entry > (out2$date.entry[nrow(out2)]-365.25)))
cat(paste0(ls,collapse="\n"))
```

# 3) Compute Limit Price For Entry and Exit
```{r}
etf_realtime = etf[,c("ETF","Exchange")]

# define new columns
etf_realtime$live_price  = NA
etf_realtime$buy_signal  = NA
etf_realtime$buy_limit   = NA
etf_realtime$sell_signal = NA
etf_realtime$sell_limit  = NA

for (i in 1:nrow(etf_realtime)) {
  
  # load data
  etf_NZ = read.csv(paste0("data/",etf$ETF[i],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  etf_id = read.csv(paste0("data/",etf$Index[i],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")

  # get currency data
  if (etf$Exchange[i] == "NYSEARCA") {
    fx = read.csv(paste0("data/NZDUSD.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  } else if (etf$Exchange[i] == "LON") {
    fx = read.csv(paste0("data/NZDGBP.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  } else if (etf$Exchange[i] == "ASX") {
    fx = read.csv(paste0("data/NZDAUD.csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  }
  
  # dates
  etf_NZ$date = as.Date(etf_NZ$date)
  etf_id$date = as.Date(etf_id$date)
  fx$date     = as.Date(fx$date)
  
  # get last 20 data
  etf_NZ = etf_NZ[(nrow(etf_NZ)-25):nrow(etf_NZ),]
  etf_id = etf_id[(nrow(etf_id)-25):nrow(etf_id),]
  fx     = fx[(nrow(fx)-25):nrow(fx),]
  
  # compute cumulative prices
  rn       = 5
  cum_nz   = rcma(etf_NZ$close,rn)
  cum_id   = rcma(etf_id$close,rn)
  cum_diff = cum_id - cum_nz
  cum_fx   = rcma(fx$close,rn)
  
  # higher filter
  rn2       = 22
  cum_nz2   = rcma(etf_NZ$close,rn2)
  cum_id2   = rcma(etf_id$close,rn2)
  cum_diff2 = cum_id2 - cum_nz2
  
  # live price
  etf_realtime$live_price[i] = tail(etf_NZ$close,1)
  
  # compute entries and exits
  etf_realtime$buy_signal[i]  = tail(crossover(1.5,cum_diff) & cum_diff2 > 0.5,1)
  etf_realtime$sell_signal[i] = tail(crossover(cum_diff,-1.0),1)
  
  # calculate threshold value for crossover
  n = nrow(etf_NZ)
  etf_realtime$buy_limit[i]  = (cum_id[n] - 1.5)*etf_NZ$close[n-4]/100 + etf_NZ$close[n-4] # 1.5 entry thres
  etf_realtime$sell_limit[i] = (cum_id[n] + 1.0)*etf_NZ$close[n-4]/100 + etf_NZ$close[n-4] # -0.1 exit thres
  
  # save plot
  plot_etf(data      = etf_NZ[6:n,],
           data_ref  = etf_id$close[6:n]/etf_id$close[6]*etf_NZ$close[6],
           data_diff = cum_diff[6:n],
           data_fx   = cum_fx[6:n],
           ind_entry = c(), ind_exit = c(),
           save = TRUE, savename = paste0("today plots/",etf$ETF[i]," - ",etf$Index[i]))

}

# Summarize Current Status
Current_Status = etf_realtime[order(etf_realtime$ETF),]
View(Current_Status)
```
