
# -------------------------------------------------------------------------------------------------------------
# Notes for NYSE + NASDAQ:
# -------------------------------------------------------------------------------------------------------------
# - Update ticker list once every 3 months (code uses min 100 data values)
# - Update database once every 3 months (code uses min 100 data values)
# 
# Processing Times:
# - 80 minutes to re-download all stocks
# - 80 minutes to update market caps and floats
# -------------------------------------------------------------------------------------------------------------
# Notes for NZX:
# -------------------------------------------------------------------------------------------------------------
# - Run code before US opens (opens after midnight)
# -------------------------------------------------------------------------------------------------------------

```{r}
rm(list=ls())
library(tidyquant)

desktop_path = file.path(Sys.getenv("USERPROFILE"),"Desktop")

# create folder to save stocks
dir.create(file.path(desktop_path,"NYSE"))
dir.create(file.path(desktop_path,"NASDAQ"))
dir.create(file.path(desktop_path,"NZX"))

# set up stocks list for both exchanges
nyse_stocks   = read.csv("NYSE.csv")
nasdaq_stocks = read.csv("NASDAQ.csv")
nzx_stocks    = read.csv("NZX.csv")

# set up NZ tickers for yahoo finance
nzx_stocks$Symbol = paste0(nzx_stocks$Symbol,".NZ")

# combine stocks into one dataframe
stocks = rbind(nyse_stocks[,c("Symbol","Cap","Float")],
               nasdaq_stocks[,c("Symbol","Cap","Float")],
               nzx_stocks[,c("Symbol","Cap","Float")])
stocks$exchange = c(rep("NYSE",nrow(nyse_stocks)),
                    rep("NASDAQ",nrow(nasdaq_stocks)),
                    rep("NZX",nrow(nzx_stocks)))
stocks$exists = FALSE

# loop through all data and save
for (i in 1:nrow(stocks)) {
  
  # show progress
  print(paste0(i," - ",stocks$Symbol[i]))
  
  # quant mod command to access yahoo finance
  df = tryCatch({
                  getSymbols(stocks$Symbol[i],
                             from="2010-01-01",
                             to=Sys.Date(),
                             warnings=FALSE,auto.assign=FALSE)
                }, 
                  error = function(cond) {
                    return(NA)
                })
  
   # whether or not stock was correctly downloaded, write if downloaded, skip if not
  if (any(is.na(df)) & stocks$exchange[i] != "NZX") { # if current has missing valus and is not NZ stock
    next
  } else if (is.null(nrow(df))) { # if current stock doesnt exist
    next
  } else if (nrow(df) <= 1) { # if there is only one row of data
    next
  } else { # record stock was correctly downloaded
    stocks$exists[i] = TRUE
  }
  
  # process data downloaded into right form
  df           = data.frame(df)
  df$Date      = rownames(df)
  rownames(df) = NULL
  colnames(df) = c("open","high","low","close","volume","close.adj","date")
  df           = df[,c("date","open","high","low","close","volume")]

  # fill in NA rows
  df[which(is.na(df$close)),2:6] = df[which(is.na(df$close))+1,2:6]
  
  # dont save stock if there is still missing value
  #if (any(is.na(df))) {
  #  stocks$exists[i] = FALSE
  #  next
  #}

  # save path
  savepath = file.path(desktop_path,stocks$exchange[i],paste0(stocks$Symbol[i],".csv"))
  
  # save stock to file
  write.csv(df,savepath,row.names=FALSE)
  
}
```

# Compute Pairwise Statistics
```{r}
f_nyse   = list.files(file.path(desktop_path,"NYSE"))
f_nasdaq = list.files(file.path(desktop_path,"NASDAQ"))

out1 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))
out2 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))
out3 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))

for (x in 1:length(f_nyse)) {
  for (y in 1:length(f_nasdaq)) {
    
    print(paste0(x," - ",y))
    
    us1_df = read.csv(file.path(desktop_path,"NYSE",f_nyse[x]),sep=",")
    us2_df = read.csv(file.path(desktop_path,"NASDAQ",f_nasdaq[y]),sep=",")
    
    if (nrow(us1_df) > nrow(us2_df)) {
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
    } else {
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
    }
    
    # compute techinical indicators
    rn       = 5
    cum_us1  = rcma(us1_df$close,rn)
    cum_us2  = rcma(us2_df$close,rn)
    cum_diff = cum_us1 - cum_us2
    
    rn2       = 22
    cum_us21  = rcma(us1_df$close,rn2)
    cum_nz22  = rcma(us2_df$close,rn2)
    cum_diff2 = cum_us21 - cum_nz22
    
    # initialize array for storage
    out_ticker      = c()
    out_exchange    = c()
    out_ind_entry   = c()
    out_ind_exit    = c()
    out_date_entry  = c()
    out_date_exit   = c()
    out_price_entry = c()
    out_price_exit  = c()
    out_return      = c()
    
    # entry indices
    ind = which(crossover(1.5,cum_diff) & cum_diff2 > 0.5)                  # ********** TUNENABLE x2
    
    # loop through every trade and apply strategy
    for (i in ind) {
      
      # set entry price
      price_entry = us2_df$close[i]
      
      # exit criteria
      ind_exit = crossover(cum_diff[i:length(cum_diff)],-1.0)             # ********** TUNENABLE
      ind_exit = which(ind_exit)[1] + i - 1
    
      # if no exit then skip trade
      if (is.na(ind_exit)) next

      # compute exit price
      price_exit = us2_df$close[ind_exit]
      
      # compute return
      return = (price_exit - price_entry)/price_entry*100
      
      # store outputs
      #out_ticker      = c(out_ticker,      etf$ETF[n])
      #out_exchange    = c(out_exchange,    etf$Exchange[n])
      out_ind_entry   = c(out_ind_entry,   i)
      out_ind_exit    = c(out_ind_exit,    ind_exit)
      out_date_entry  = c(out_date_entry,  as.character(us2_df$date[i]))
      out_date_exit   = c(out_date_exit,   as.character(us2_df$date[ind_exit]))
      out_price_entry = c(out_price_entry, price_entry)
      out_price_exit  = c(out_price_exit,  price_exit)
      out_return      = c(out_return,      return)
      
    }
    
    # store all trades
    out = data.frame(#ticker      = out_ticker,
                     #exchange    = out_exchange,
                     ind.entry   = out_ind_entry,
                     ind.exit    = out_ind_exit,
                     date.entry  = as.Date(out_date_entry),
                     date.exit   = as.Date(out_date_exit),
                     price.entry = out_price_entry,
                     price.exit  = out_price_exit,
                     return      = out_return)
    
    # apply comission
    #out$return = out$return - 0.5
    out = out[!is.na(out$return),]
    out$outcome = ifelse(out$return > 0, TRUE, FALSE)

    # save
    out1[x,y] = sum(out$outcome)/nrow(out)*100
    out2[x,y] = sum(out$outcome)*mean(out$return[out$outcome])/nrow(out) + sum(!out$outcome)*mean(out$return[!out$outcome])/nrow(out)
    out3[x,y] = unname(cor.test(us1_df$close,us2_df$close)$estimate) # pearson correlation
    
  }
}

colnames(out1) = gsub(".csv","",f_nasdaq)
rownames(out1) = gsub(".csv","",f_nyse)

colnames(out2) = gsub(".csv","",f_nasdaq)
rownames(out2) = gsub(".csv","",f_nyse)

colnames(out3) = gsub(".csv","",f_nasdaq)
rownames(out3) = gsub(".csv","",f_nyse)

write.csv(out1,"1_win_rates.csv")
write.csv(out2,"2_expecations.csv")
write.csv(out3,"3_correlation.csv")
```


# Load all important info (takes a while)
```{r}
# important pairwise info
out1 = read.csv("1 - win rates.csv",header=TRUE)
row.names(out1) = out1$X
out1 = out1[,-1]

out2 = read.csv("2 - expecations.csv",header=TRUE)
row.names(out2) = out2$X
out2 = out2[,-1]

out3 = read.csv("3 - correlation.csv",header=TRUE)
row.names(out3) = out3$X
out3 = out3[,-1]

# set up file paths for NYSE and NASDAQ
f_nyse = list.files(file.path(desktop_path,"NYSE"))
f_nasdaq = list.files(file.path(desktop_path,"NASDAQ"))

# loop through both and compute number of rows for each individual stock
nyse_n = rep(NA,length(f_nyse))
nasdaq_n = rep(NA,length(f_nasdaq))

for (i in 1:length(nyse_n)) {
  nyse_n[i] = nrow(read.csv(file.path(desktop_path,"NYSE",f_nyse[i]),sep=","))
}

for (i in 1:length(nasdaq_n)) {
  nasdaq_n[i] = nrow(read.csv(file.path(desktop_path,"NASDAQ",f_nasdaq[i]),sep=","))
}

# store names, rowname = stock, row content = number of samples
nyse_n = data.frame(nyse_n)
rownames(nyse_n) = gsub(".csv","",f_nyse)

nasdaq_n = data.frame(nasdaq_n)
rownames(nasdaq_n) = gsub(".csv","",f_nasdaq)
```

# Find Pairs To Trade
```{r}
# 0.99 is optimal for simulation
median(out2[out3 >= 0.99], na.rm=TRUE)

# get stocks with high overall correlations
ind = which(out3 >= 0.99, arr.ind=TRUE)
rownames(ind) = NULL

# col 1 = NYSE, col 2 = NASDAQ
pairs = cbind(rownames(out1)[ind[,1]], colnames(out1)[ind[,2]])
colnames(pairs) = c("NYSE","NASDAQ")

# filter out stocks with small number of samples
col1_n = nyse_n[pairs[,1],]
col2_n = nasdaq_n[pairs[,2],]

pairs = pairs[col1_n > 250 & col2_n > 250,]

# write to output
#write.csv(pairs,"pairs.csv",row.names=FALSE)
```
