
# --------------------------------------------------------------------------------------
# IBKR Fees
# --------------------------------------------------------------------------------------
# Stocks: 
#     - 0.005 USD/share                 (Shares above or equal to 0.5 USD)
#     - 1% of trade value               (Shares below 0.5 USD)
#     - Minimum of 1 USD for any trade  (When trading less than 200 shares of any stock)
# # 
# Currency:
#     - 0.002% of trade value           (When trading above or equals to 100,000 USD)
#     - Minimum of 2 USD for any trade  (When trading less than 100,000 USD)
# # 
# --------------------------------------------------------------------------------------

# helper functions
```{r}
rm(list=ls())
#setwd("C:/Users/zxio506/OneDrive/Assets/Securities/Trading Stocks")

# path to stocks
desktop_path = file.path(Sys.getenv("USERPROFILE"),"Desktop")

# rolling cumulative return moving average
rcma = function(x,n) {
  
  n     = n - 1
  rma_x = (x[1:n]-x[1])/x[1]

  for (i in seq(1, length(x)-n)) {
    rma_x = c(rma_x, (x[i+n]-x[i])/x[i])
  }
  
  return(rma_x*100)

}

# compute location of cross over
crossover = function(x1,x2) {
  
  # find max time steps
  l = max(c(length(x1),length(x2)))
  
  # duplicate values if only singular numeric value is provided
  if (length(x1) == 1) x1 = rep(x1,l)
  if (length(x2) == 1) x2 = rep(x2,l)
  
  # find which indices are true, if NA then set as false. x1 was more, now is less
  cross_ind = c(FALSE,x1[1:(l-1)] > x2[1:(l-1)] & x1[2:l] < x2[2:l])
  cross_ind[is.na(cross_ind)] = FALSE
  
  return(cross_ind)
  
}

# plot ticker
plot_etf = function(data,data_ref,data_diff,
                    ind_entry,ind_exit,
                    save=FALSE,savename="") {
  
  # save plot
  if (save) png(paste0(savename,".png"), width = 500, height = 750)
  
  # set up plot area
  layout(matrix(1:2,2,1),heights=c(1.5,1))
  
  # set up plot range
  xrange = range(data$date,na.rm=TRUE)
  yrange = range(c(data$high*1.005,data$low*0.995,data_ref),na.rm=TRUE)
  
  # initialize plot with margin sizes
  par(mar=c(1,4,1,1))
  plot(-999,-999,xlim=xrange,ylim=yrange,xlab="",ylab="Price (NZD)",xaxt="n",yaxt="n")
  
  # label axis
  axis(2,at=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),
       labels=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),las=2)
  
  # reference index price
  lines(data$date,data_ref,col="orange")
  points(data$date,data_ref,col="orange",pch=20)
  
  # insert candlesticks
  abline(v=data$date,col="grey80",lty=4)
  colors = ifelse(data$close >= data$open,"forestgreen","tomato")
  segments(x0  = data$date, y0 = data$low
          ,x1  = data$date, y1 = data$high
          ,col = colors, lwd=1
  )
  rect(xleft   = data$date-0.3
      ,ybottom = ifelse(data$close >= data$open,data$open,data$close)
      ,xright  = data$date+0.3
      ,ytop    = ifelse(data$close >= data$open,data$close,data$open)
      ,col     = colors,border=colors
  )
  
  # plot entry and exit
  points(data$date[ind_entry],data$low[ind_entry]*0.995,col="blue",pch=24,cex=2,lwd=3)
  points(data$date[ind_exit],data$high[ind_exit]*1.005,col="blue",pch=25,cex=2,lwd=3)
  
  # set up plot range
  yrange2 = range(data_diff,na.rm=TRUE)
  
  # initialize plot with margin sizes
  par(mar=c(6,4,0,1))
  plot(-999,-999,xlim=xrange,ylim=yrange2,xlab="",ylab= "Index - Stock",xaxt="n",las=1)
  
  # label axis
  axis(1,at=seq(xrange[1],xrange[2],by=1),labels=seq(xrange[1],xrange[2],by=1),las=2)
  
  # add diff plot
  abline(h=-10:10,col="grey80",lty=4)
  abline(v=data$date,col="grey80",lty=4)
  abline(h=c(1.5,-1.0),col="deepskyblue",lty=2,lwd=2)
  
  lines(data$date,data_diff,col="black")
  points(data$date,data_diff,col="black",pch=20)
  
  # save plot
  if (save) dev.off()
  
}
```

# Simulate All Trades
```{r}
pairs = read.csv("pairs.csv",header=TRUE)

# store data
out_ticker_base = c()
out_ticker_comp = c()
out_exchange    = c()
out_ind_entry   = c()
out_ind_exit    = c()
out_date_entry  = c()
out_date_exit   = c()
out_price_entry = c()
out_price_exit  = c()
out_return      = c()

# which exchange to trade, 1 for NYSE trading, 2 for NASDAQ trading
exchange = c("NYSE","NASDAQ")

for (key in 1:2) {
  
  # loop through every ETF pair
  for (n in 1:nrow(pairs)) {
    
    # load data
    etf_ny = read.csv(paste0(file.path(desktop_path,exchange[key]),"/",pairs[n,key],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
    etf_nq = read.csv(paste0(file.path(desktop_path,exchange[3-key]),"/",pairs[n,3-key],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
    
    etf_ny$date = as.Date(etf_ny$date)
    etf_nq$date = as.Date(etf_nq$date)
  
    # normalize number of rows
    if (nrow(etf_ny) > nrow(etf_nq)) {
      etf_ny = etf_ny[(nrow(etf_ny)-nrow(etf_nq)+1):nrow(etf_ny),]
      etf_nq = etf_nq[(nrow(etf_nq)-nrow(etf_ny)+1):nrow(etf_nq),]
    } else {
      etf_nq = etf_nq[(nrow(etf_nq)-nrow(etf_ny)+1):nrow(etf_nq),]
      etf_ny = etf_ny[(nrow(etf_ny)-nrow(etf_nq)+1):nrow(etf_ny),]
    }
    
    # compute cumulative prices
    rn       = 5
    cum_nz   = rcma(etf_ny$close,rn) # nz = base stock to trade
    cum_id   = rcma(etf_nq$close,rn) # id = stock to compare against
    cum_diff = cum_id - cum_nz
  
    # higher filter
    rn2       = 22
    cum_nz2   = rcma(etf_ny$close,rn2)
    cum_id2   = rcma(etf_nq$close,rn2)
    cum_diff2 = cum_id2 - cum_nz2
    
    # entry indices
    ind = which(crossover(1.5,cum_diff) & cum_diff2 > 1.5)                # ********** TUNENABLE x2
    
    # loop through every trade and apply strategy
    for (i in ind) {
      
      # set entry price
      price_entry = etf_ny$close[i]
      
      # exit criteria
      ind_exit = crossover(cum_diff[i:length(cum_diff)],-1.0)             # ********** TUNENABLE
      ind_exit = which(ind_exit)[1] + i - 1
  
      # if no exit then skip trade
      if (is.na(ind_exit)) next
  
      # compute exit price
      price_exit = etf_ny$close[ind_exit]
      
      # compute return
      return = (price_exit - price_entry)/price_entry*100
  
      # store outputs
      out_ticker_base = c(out_ticker_base, pairs[n,key])
      out_ticker_comp = c(out_ticker_comp, pairs[n,3-key])
      out_exchange    = c(out_exchange,    exchange[key])
      out_ind_entry   = c(out_ind_entry,   i)
      out_ind_exit    = c(out_ind_exit,    ind_exit)
      out_date_entry  = c(out_date_entry,  as.character(etf_ny$date[i]))
      out_date_exit   = c(out_date_exit,   as.character(etf_ny$date[ind_exit]))
      out_price_entry = c(out_price_entry, price_entry)
      out_price_exit  = c(out_price_exit,  price_exit)
      out_return      = c(out_return,      return)
      
    }
    
  }
}

# store all trades
out = data.frame(ticker_base = out_ticker_base,
                 ticker_comp = out_ticker_comp,
                 exchange    = out_exchange,
                 ind.entry   = out_ind_entry,
                 ind.exit    = out_ind_exit,
                 date.entry  = as.Date(out_date_entry),
                 date.exit   = as.Date(out_date_exit),
                 price.entry = out_price_entry,
                 price.exit  = out_price_exit,
                 return      = out_return)

# combine tickers into one column
out$ticker = paste0(out$ticker_base,"_",out$ticker_comp)

# apply comission (0.005 USD/share, max 1% of trade, minimum 1 USD per trade)
capital = 10000 # account balance
buy_comission = pmin(1, pmax(1/capital*100, capital/out$price.entry*0.005/capital*100))
sell_comission = pmin(1, pmax(1/capital*100, capital/out$price.exit*0.005/capital*100))
round_trip_comission = buy_comission + sell_comission
out$return = out$return - round_trip_comission

# compute outcome column (win or lose)
out = out[!is.na(out$return),]
out$outcome = ifelse(out$return > 0, TRUE, FALSE)

# Summarize
ls = list()
ls[[1]] = sprintf("---------------------------")
ls[[2]] = sprintf("Avg Win:  %0.2f%%", mean(out$return[out$outcome]))
ls[[3]] = sprintf("Avg Loss: %0.2f%%", mean(out$return[!out$outcome]))
ls[[4]] = sprintf("Win Rate: %0.1f%%", sum(out$outcome)/nrow(out)*100)
ls[[5]] = sprintf("Expected: %0.2f%%", sum(out$outcome)*mean(out$return[out$outcome])/nrow(out) + 
                                           sum(!out$outcome)*mean(out$return[!out$outcome])/nrow(out))
ls[[6]] = sprintf("Avg Hold Period: %0.1f Days", mean(out$ind.exit-out$ind.entry))
cat(paste0(ls,collapse="\n"))

# Summarize Tickers By Individual Win Rates
# temp = aggregate(out[,c(10,12)], by = list(out$ticker,out$exchange), FUN = mean)
# temp = temp[order(temp$Group.1),]
# temp$n = table(out$ticker)
# View(temp)
```

# Simulate Portfolio
```{r}
# sort by date and define new dataframe, with coutners
out_real          = out[order(out$date.entry),]
out_real$real     = FALSE
out_real$active   = FALSE
out_real$n_active = NA
max_active        = 10

for (i in 1:nrow(out_real)) {

  # exit previous positions which has passed
  out_real$active[out_real$date.entry[i] > out_real$date.exit] = FALSE
  
  # if there are still position slots available
  if (sum(out_real$active) < max_active) {
    out_real$active[i] = TRUE
    out_real$real[i]   = TRUE
  }

  # calcualte total number of active trades
  out_real$n_active[i] = sum(out_real$active)
  
}

# filter trades executed, and adjust return per trade due to position sizing
out_real = out_real[out_real$real,]
out_real$return = out_real$return/max_active

par(mfrow=c(2,1)) 

# plot portfolio performance
cum_port = cumprod(out_real$return/100+1)

plot(out_real$date.entry,cum_port,type="l",log="y")
abline(h=c(1:10,seq(10,100,by=10)),lty=2, col="grey50")
abline(v=as.Date(paste0(2009:2025,"-01-01")),lty=2, col="grey50")
lines(out_real$date.entry,cum_port,col="blue",lwd=2)

# plot annual return
yearly_return = c()
for (i in 2010:2021) {
  
  year_i = as.Date(paste0(i,"-01-01"))
  start_i = cum_port[which(out_real$date.entry >= year_i)[1]]
  end_i = cum_port[tail(which(out_real$date.entry <= (year_i+366)),1)]
  return_i = (end_i - start_i)/start_i*100
  yearly_return = c(yearly_return,return_i)
  
}

names(yearly_return) = 2010:2021
barplot(yearly_return)
abline(h=seq(round(min(yearly_return),-1),round(max(yearly_return),-1),by=10),lty=2,col="grey50")

# Summarize
ls = list()
ls[[1]] = sprintf("---------------------------")
ls[[2]] = sprintf("Win Rate: %0.1f%%",           sum(out_real$outcome)/nrow(out_real)*100)
ls[[3]] = sprintf("Expected: %0.2f%%",           (sum(out_real$outcome)*mean(out_real$return[out_real$outcome])/nrow(out_real) + 
                                                   sum(!out_real$outcome)*mean(out_real$return[!out_real$outcome])/nrow(out_real))*max_active)
ls[[4]] = sprintf("Avg Hold Period: %0.1f Days", mean(out_real$ind.exit-out_real$ind.entry))
ls[[5]] = sprintf("Trades Per Year: %0.0f",      sum(out_real$date.entry > (out_real$date.entry[nrow(out_real)]-365.25)))
ls[[6]] = sprintf("Annualized Return: %0.1f%%",  ((1+tail(cum_port,1))^
                                                   (365/as.numeric((out_real$date.exit[nrow(out_real)]-out_real$date.entry[1])))-1)*100)
ls[[7]] = sprintf("Median Annual Return: %0.1f%%", median(yearly_return))
cat(paste0(ls,collapse="\n"))
```



# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # 



# Compute Potential NYSE Trades
```{r}
# first run initialization block
# initialize dataframe 
pairs_trade_nyse = read.csv("pairs.csv",header=TRUE)

# define new columns
pairs_trade_nyse$live_price  = NA
pairs_trade_nyse$buy_signal  = NA
pairs_trade_nyse$buy_limit   = NA
pairs_trade_nyse$sell_signal = NA
pairs_trade_nyse$sell_limit  = NA

# trade nyse
for (i in 1:nrow(pairs_trade_nyse)) {
  
  # load data
  us_tr = read.csv(paste0(file.path(desktop_path,"NYSE"),"/",pairs_trade_nyse[i,1],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  us_id = read.csv(paste0(file.path(desktop_path,"NASDAQ"),"/",pairs_trade_nyse[i,2],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  
  # dates
  us_tr$date = as.Date(us_tr$date)
  us_id$date = as.Date(us_id$date)

  # get last 20 data
  us_tr = us_tr[(nrow(us_tr)-25):nrow(us_tr),]
  us_id = us_id[(nrow(us_id)-25):nrow(us_id),]
  
  # compute cumulative prices
  rn       = 5
  cum_nz   = rcma(us_tr$close,rn)
  cum_id   = rcma(us_id$close,rn)
  cum_diff = cum_id - cum_nz

  # higher filter
  rn2       = 22
  cum_nz2   = rcma(us_tr$close,rn2)
  cum_id2   = rcma(us_id$close,rn2)
  cum_diff2 = cum_id2 - cum_nz2
  
  # live price
  pairs_trade_nyse$live_price[i] = tail(us_tr$close,1)
  
  # compute entries and exits
  pairs_trade_nyse$buy_signal[i]  = tail(crossover(1.5,cum_diff) & cum_diff2 > 1.5,1)
  pairs_trade_nyse$sell_signal[i] = tail(crossover(cum_diff,-1.0),1)
  
  # calculate threshold value for crossover
  n = nrow(us_tr)
  pairs_trade_nyse$buy_limit[i]  = (cum_id[n] - 1.5)*us_tr$close[n-4]/100 + us_tr$close[n-4] # 1.5 entry thres
  pairs_trade_nyse$sell_limit[i] = (cum_id[n] + 1.0)*us_tr$close[n-4]/100 + us_tr$close[n-4] # -1.0 exit thres
  
  # save plot
  plot_etf(data      = us_tr[6:n,],
           data_ref  = us_id$close[6:n]/us_id$close[6]*us_tr$close[6],
           data_diff = cum_diff[6:n],
           ind_entry = c(), ind_exit = c(),
           save = TRUE, savename = paste0("nyse plot/",pairs_trade_nyse$NYSE[i],"-",pairs_trade_nyse$NASDAQ[i]))

}

# Summarize Current Status
NYSE_Status = pairs_trade_nyse[order(pairs_trade_nyse$NYSE),]
View(NYSE_Status)
```
# Compute NASDAQ Trades
```{r}
# define same dataframe for nasdaq
pairs_trade_nasdaq = pairs_trade_nyse[,c(2,1,3:ncol(pairs_trade_nyse))]
pairs_trade_nasdaq[,3:ncol(pairs_trade_nasdaq)] = NA

# trade nyse
for (i in 1:nrow(pairs_trade_nasdaq)) {
  
  # load data
  us_tr = read.csv(paste0(file.path(desktop_path,"NASDAQ"),"/",pairs_trade_nasdaq[i,1],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  us_id = read.csv(paste0(file.path(desktop_path,"NYSE"),"/",pairs_trade_nasdaq[i,2],".csv"),header=TRUE,stringsAsFactors=FALSE,sep=",")
  
  # dates
  us_tr$date = as.Date(us_tr$date)
  us_id$date = as.Date(us_id$date)

  # get last 20 data
  us_tr = us_tr[(nrow(us_tr)-25):nrow(us_tr),]
  us_id = us_id[(nrow(us_id)-25):nrow(us_id),]
  
  # compute cumulative prices
  rn       = 5
  cum_nz   = rcma(us_tr$close,rn)
  cum_id   = rcma(us_id$close,rn)
  cum_diff = cum_id - cum_nz

  # higher filter
  rn2       = 22
  cum_nz2   = rcma(us_tr$close,rn2)
  cum_id2   = rcma(us_id$close,rn2)
  cum_diff2 = cum_id2 - cum_nz2
  
  # live price
  pairs_trade_nasdaq$live_price[i] = tail(us_tr$close,1)
  
  # compute entries and exits
  pairs_trade_nasdaq$buy_signal[i]  = tail(crossover(1.5,cum_diff) & cum_diff2 > 1.5,1)
  pairs_trade_nasdaq$sell_signal[i] = tail(crossover(cum_diff,-1.0),1)
  
  # calculate threshold value for crossover
  n = nrow(us_tr)
  pairs_trade_nasdaq$buy_limit[i]  = (cum_id[n] - 1.5)*us_tr$close[n-4]/100 + us_tr$close[n-4] # 1.5 entry thres
  pairs_trade_nasdaq$sell_limit[i] = (cum_id[n] + 1.0)*us_tr$close[n-4]/100 + us_tr$close[n-4] # -1.0 exit thres
  
  # save plot
  plot_etf(data      = us_tr[6:n,],
           data_ref  = us_id$close[6:n]/us_id$close[6]*us_tr$close[6],
           data_diff = cum_diff[6:n],
           ind_entry = c(), ind_exit = c(),
           save = TRUE, savename = paste0("nasdaq plot/",pairs_trade_nasdaq$NASDAQ[i],"-",pairs_trade_nasdaq$NYSE[i]))

}

# Summarize Current Status
NASDAQ_Status = pairs_trade_nasdaq[order(pairs_trade_nasdaq$NASDAQ),]
View(NASDAQ_Status)
```