
--------------------------------------------------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------------------------------------------------

# Summarize Win Rate
```{r}
out1 = read.csv("1 - win rates.csv",header=TRUE)
row.names(out1) = out1$X
out1 = out1[,-1]

hist(unlist(out1))
median(unlist(out1),na.rm=TRUE)
```

# Summarize Expectations
```{r}
out2 = read.csv("2 - expecations.csv",header=TRUE)
row.names(out2) = out2$X
out2 = out2[,-1]

p95 = quantile(out2,0.95, na.rm=TRUE)
p05 = quantile(out2,0.05, na.rm=TRUE)
temp = out2[out2 <= p95 & out2 >= p05]
hist(temp)
median(temp,na.rm=TRUE)
```

# Investigate Correlation
```{r}
out3 = read.csv("3 - correlation.csv",header=TRUE)
row.names(out3) = out3$X
out3 = out3[,-1]

median(unlist(out2)[unlist(out3) > 0.9],na.rm=TRUE)

```

# Plot Two Stocks
```{r}
desktop_path = file.path(Sys.getenv("USERPROFILE"),"Desktop")

df1 = read.csv(file.path(desktop_path,"NYSE","KTB.csv"),sep=",")
df2 = read.csv(file.path(desktop_path,"NASDAQ","AACG.csv"),sep=",")

if (nrow(df1) > nrow(df2)) {
  df1 = df1[(nrow(df1)-nrow(df2)+1):nrow(df1),]
  df2 = df2[(nrow(df2)-nrow(df1)+1):nrow(df2),]
} else {
  df2 = df2[(nrow(df2)-nrow(df1)+1):nrow(df2),]
  df1 = df1[(nrow(df1)-nrow(df2)+1):nrow(df1),]
}

p1 = (df1$close-min(df1$close))/max(df1$close-min(df1$close))
p2 = (df2$close-min(df2$close))/max(df2$close-min(df2$close))
cor.test(p1,p2)

dtw(p1,p2)$normalizedDistance

#plot(p2,type="l")
#lines(p1,col="blue")
```

- find a good correlation metric (dwt?)
- compute relation of correlation and expectation
- compute relation of market cap (pair??) and expectation

- simulate portfolio somehow (need to compute correlation each time as well)








# 0) Initialize Functions and Load Ticker List
```{r}
rm(list=ls())
library(dtw)

desktop_path = file.path(Sys.getenv("USERPROFILE"),"Desktop")

# load stocks
nasdaq = read.csv("NASDAQ.csv",header=TRUE)
nyse   = read.csv("NYSE.csv",header=TRUE)

# rolling cumulative return moving average
rcma = function(x,n) {
  
  n     = n - 1
  rma_x = (x[1:n]-x[1])/x[1]

  for (i in seq(1, length(x)-n)) {
    rma_x = c(rma_x, (x[i+n]-x[i])/x[i])
  }
  
  return(rma_x*100)
  
}

# compute location of cross over
crossover = function(x1,x2) {
  
  # find max time steps
  l = max(c(length(x1),length(x2)))
  
  # duplicate values if only singular numeric value is provided
  if (length(x1) == 1) x1 = rep(x1,l)
  if (length(x2) == 1) x2 = rep(x2,l)
  
  # find which indices are true, if NA then set as false. x1 was more, now is less
  cross_ind = c(FALSE,x1[1:(l-1)] > x2[1:(l-1)] & x1[2:l] < x2[2:l])
  cross_ind[is.na(cross_ind)] = FALSE
  
  return(cross_ind)
  
}

# plot ticker
plot_etf = function(data,data_ref,data_diff,data_fx,
                    ind_entry,ind_exit,
                    save=FALSE,savename="") {
  
  # save plot
  if (save) png(paste0(savename,".png"), width = 500, height = 750)
  
  # set up plot area
  layout(matrix(1:2,2,1),heights=c(1.5,1))
  
  # set up plot range
  xrange = range(data$date)
  yrange = range(c(data$high*1.005,data$low*0.995,data_ref))
  
  # initialize plot with margin sizes
  par(mar=c(1,4,1,1))
  plot(-999,-999,xlim=xrange,ylim=yrange,xlab="",ylab="Price (NZD)",xaxt="n",yaxt="n")
  
  # label axis
  axis(2,at=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),
       labels=round(seq(yrange[1]*0.9,yrange[2]*1.1,by=0.01),2),las=2)
  
  # reference index price
  lines(data$date,data_ref,col="orange")
  points(data$date,data_ref,col="orange",pch=20)
  
  # insert candlesticks
  abline(v=data$date,col="grey80",lty=4)
  colors = ifelse(data$close >= data$open,"forestgreen","tomato")
  segments(x0  = data$date, y0 = data$low
          ,x1  = data$date, y1 = data$high
          ,col = colors, lwd=1
  )
  rect(xleft   = data$date-0.3
      ,ybottom = ifelse(data$close >= data$open,data$open,data$close)
      ,xright  = data$date+0.3
      ,ytop    = ifelse(data$close >= data$open,data$close,data$open)
      ,col     = colors,border=colors
  )
  
  # plot entry and exit
  points(data$date[ind_entry],data$low[ind_entry]*0.995,col="blue",pch=24,cex=2,lwd=3)
  points(data$date[ind_exit],data$high[ind_exit]*1.005,col="blue",pch=25,cex=2,lwd=3)
  
  # set up plot range
  yrange2 = range(c(data_diff,data_fx),na.rm=TRUE)
  
  # initialize plot with margin sizes
  par(mar=c(6,4,0,1))
  plot(-999,-999,xlim=xrange,ylim=yrange2,xlab="",ylab= "Index - NZ ETF",xaxt="n",las=1)
  
  # label axis
  axis(1,at=seq(xrange[1],xrange[2],by=1),labels=seq(xrange[1],xrange[2],by=1),las=2)
  
  # add diff plot
  abline(h=-10:10,col="grey80",lty=4)
  abline(v=data$date,col="grey80",lty=4)
  abline(h=c(1.5,-0.5),col="deepskyblue",lty=2)
  
  lines(data$date,data_diff,col="black")
  points(data$date,data_diff,col="black",pch=20)
  
  lines(data$date,data_fx,col="red")
  points(data$date,data_fx,col="red",pch=20)
  
  # save plot
  if (save) dev.off()
  
}
```

# Compute Winning Percentage of All Stock Pairs
```{r}
f_nyse   = list.files(file.path(desktop_path,"NYSE"))
f_nasdaq = list.files(file.path(desktop_path,"NASDAQ"))

out1 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))
out2 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))

for (x in 1:length(f_nyse)) {
  for (y in 1:length(f_nasdaq)) {
    
    print(paste0(x," - ",y))
    
    us1_df = read.csv(file.path(desktop_path,"NYSE",f_nyse[x]),sep=",")
    us2_df = read.csv(file.path(desktop_path,"NASDAQ",f_nasdaq[y]),sep=",")
    
    if (nrow(us1_df) > nrow(us2_df)) {
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
    } else {
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
    }
    
    # compute techinical indicators
    rn       = 5
    cum_us1  = rcma(us1_df$close,rn)
    cum_us2  = rcma(us2_df$close,rn)
    cum_diff = cum_us1 - cum_us2
    
    rn2       = 22
    cum_us21  = rcma(us1_df$close,rn2)
    cum_nz22  = rcma(us2_df$close,rn2)
    cum_diff2 = cum_us21 - cum_nz22
    
    # initialize array for storage
    out_ticker      = c()
    out_exchange    = c()
    out_ind_entry   = c()
    out_ind_exit    = c()
    out_date_entry  = c()
    out_date_exit   = c()
    out_price_entry = c()
    out_price_exit  = c()
    out_return      = c()
    
    # entry indices
    ind = which(crossover(1.5,cum_diff) & cum_diff2 > 0.5)                  # ********** TUNENABLE x2
    ind = which(crossover(1.5,cum_diff))
    
    # loop through every trade and apply strategy
    for (i in ind) {
      
      # set entry price
      price_entry = us2_df$close[i]
      
      # exit criteria
      ind_exit = crossover(cum_diff[i:length(cum_diff)],-1.0)             # ********** TUNENABLE
      ind_exit = which(ind_exit)[1] + i - 1
    
      # if no exit then skip trade
      if (is.na(ind_exit)) next

      # compute exit price
      price_exit = us2_df$close[ind_exit]
      
      # compute return
      return = (price_exit - price_entry)/price_entry*100
      
      # store outputs
      #out_ticker      = c(out_ticker,      etf$ETF[n])
      #out_exchange    = c(out_exchange,    etf$Exchange[n])
      out_ind_entry   = c(out_ind_entry,   i)
      out_ind_exit    = c(out_ind_exit,    ind_exit)
      out_date_entry  = c(out_date_entry,  as.character(us2_df$date[i]))
      out_date_exit   = c(out_date_exit,   as.character(us2_df$date[ind_exit]))
      out_price_entry = c(out_price_entry, price_entry)
      out_price_exit  = c(out_price_exit,  price_exit)
      out_return      = c(out_return,      return)
      
    }
    
    # store all trades
    out = data.frame(#ticker      = out_ticker,
                     #exchange    = out_exchange,
                     ind.entry   = out_ind_entry,
                     ind.exit    = out_ind_exit,
                     date.entry  = as.Date(out_date_entry),
                     date.exit   = as.Date(out_date_exit),
                     price.entry = out_price_entry,
                     price.exit  = out_price_exit,
                     return      = out_return)
    
    # apply comission
    #out$return = out$return - 0.5
    out = out[!is.na(out$return),]
    out$outcome = ifelse(out$return > 0, TRUE, FALSE)

    # save
    out1[x,y] = sum(out$outcome)/nrow(out)*100
    out2[x,y] = sum(out$outcome)*mean(out$return[out$outcome])/nrow(out) + sum(!out$outcome)*mean(out$return[!out$outcome])/nrow(out)
    
  }
}

colnames(out1) = gsub(".csv","",f_nasdaq)
rownames(out1) = gsub(".csv","",f_nyse)

colnames(out2) = gsub(".csv","",f_nasdaq)
rownames(out2) = gsub(".csv","",f_nyse)

write.csv(out1,"1 - win rates.csv")
write.csv(out2,"2 - expecations.csv")
```

# Compute Correlation Between All Stock Pairs
```{r}
f_nyse   = list.files(file.path(desktop_path,"NYSE"))
f_nasdaq = list.files(file.path(desktop_path,"NASDAQ"))

out3 = matrix(rep(NA,length(f_nyse)*length(f_nasdaq)),length(f_nyse),length(f_nasdaq))

for (x in 1:length(f_nyse)) {
  for (y in 1:length(f_nasdaq)) {
    
    print(paste0(x," - ",y))
    
    us1_df = read.csv(file.path(desktop_path,"NYSE",f_nyse[x]),sep=",")
    us2_df = read.csv(file.path(desktop_path,"NASDAQ",f_nasdaq[y]),sep=",")
    
    if (nrow(us1_df) > nrow(us2_df)) {
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
    } else {
      us2_df = us2_df[(nrow(us2_df)-nrow(us1_df)+1):nrow(us2_df),]
      us1_df = us1_df[(nrow(us1_df)-nrow(us2_df)+1):nrow(us1_df),]
    }
    
    # save
    #out3[x,y] = unname(cor.test(us1_df$close,us2_df$close)$estimate) # pearson correlation
    out3[x,y] = dtw(us1_df$close,us2_df$close)$normalizedDistance # dtw

  }
}

colnames(out3) = gsub(".csv","",f_nasdaq)
rownames(out3) = gsub(".csv","",f_nyse)

write.csv(out3,"4 - dtw.csv")
```
